---
title: "<b>Breakage - Root Cause Investigation</b>"
author: "Paul M. Washburn"
date: "YTD, 2016 & 2017"
#output: html_document
output: 
  pdf_document:
      df_print: "kable" 
      fig_width: 9
      fig_height: 8
---

```{r setup, include=FALSE, fig.height=9, fig.width=9}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
library(ggplot2)
library(scales)
library(plotly)

path = 'C:/Users/pmwash/Desktop/Re-Engineered Reports/Breakage/'
df = read.csv(paste0(path,'Clean Breakage Data.csv'), header=TRUE)
cal_df = read.csv(paste0(path,'Calendar 2016-2017.csv'))
cal_df = cal_df[, c('Date','WeekNumber','Weekday','IsWeekday','IsProductionDay',
                    'LastSellingDayOfMonth','Season','HolidayWeek','Holiday','ShipWeek')]
df = merge(df, cal_df, on='Date', how='inner')

pw_supprod = read.csv('C:/Users/pmwash/Desktop/Re-Engineered Reports/Generalized Lookup Data/pw_supprod.csv', header=T)

names(pw_supprod) = c('ProductId','X','SupplierId','Supplier')
pw_supprod$X = NULL

df = merge(df, pw_supprod, on='ProductId', how='inner')
df = df[df$ReasonCode != 'Sales Breakage & Unsaleables', ]

breakageByProduct = function(df) {
  byProduct = aggregate(cbind(df$Breakage.Dollars, df$Breakage.Cases) ~ df$ProductId + df$Product + 
                          df$SupplierId + df$Supplier, FUN=function(x) sum(x, na.rm=T))
  names(byProduct) = c('ProductId','Product','SupplierId','Supplier',
                       'BreakageDollars','BreakageCases')
  dfSales = df[(!duplicated(df$ProductId)) & (df$Sales.Dollars > 0), c('ProductId','Sales.Dollars')]
  byProduct = merge(byProduct, dfSales, by='ProductId', how='inner')
  colnames(byProduct)[ncol(byProduct)] = 'SalesDollars'
  byProduct$BreakagePctSales = round(byProduct$BreakageDollars / byProduct$SalesDollars, 5)
  ## Filter out low volume SKUs
  byProduct = byProduct[byProduct$SalesDollars >= quantile(byProduct$SalesDollars, .25), ]
  byProduct = byProduct[byProduct$BreakageDollars >= quantile(byProduct$BreakageDollars, .25), ]
  byProduct$ProductSupplier = paste0(byProduct$Product, '\n  -  ', byProduct$Supplier, '\n')
  byProduct$SalesVsBreakage = paste0('  -  Sales = ',as.character(round(byProduct$SalesDollars, 0)),
                                     '\n  -  Breakage = ', as.character(round(byProduct$BreakageDollars, 0)),
                                     '\n  -  Percent of Sales = ', as.character(round(byProduct$BreakageDollars / byProduct$SalesDollars, 4)*100), '%')
  byProduct$ProductSummary = paste0(byProduct$ProductSupplier, byProduct$SalesVsBreakage)
  return(byProduct)
}

"%!in%" <- function(x,table) match(x,table, nomatch = 0) == 0

byProduct = breakageByProduct(df)

extractSignificantSuppliers = function(byProduct){
  sumLinmod = summary(lm(BreakageDollars ~ SalesDollars + Supplier, data=byProduct))$coefficients
  dfCoefficients = data.frame(tScore=sumLinmod[sumLinmod[, 'Pr(>|t|)'] <= .05,'Pr(>|t|)'])
  significantCategories = rownames(dfCoefficients)
  significantCategories = significantCategories[significantCategories %!in% 'SalesDollars']
  significantCategories = gsub('Supplier','',significantCategories)
  return(significantCategories)
}


extractSignificantProducts = function(byProduct){
  sumLinmod = summary(lm(BreakageDollars ~ SalesDollars + Product, data=byProduct))$coefficients
  dfCoefficients = data.frame(tScore=sumLinmod[sumLinmod[, 'Pr(>|t|)'] <= .05,'Pr(>|t|)'])
  significantCategories = rownames(dfCoefficients)
  significantCategories = significantCategories[significantCategories %!in% 'SalesDollars']
  significantCategories = gsub('Product','',significantCategories)
  return(significantCategories)
}

engineerFeatures = function(byProduct, df){
  byProduct$ExtremeBreakageSupplier = byProduct$Supplier %in% extractSignificantSuppliers(byProduct)
  byProduct$ExtremeBreakageProduct = byProduct$Product %in% extractSignificantProducts(byProduct)
  byProduct$ExtremeBreakageProductOrSupplier = idNonHigh = byProduct$ExtremeBreakageProduct | byProduct$ExtremeBreakageSupplier 
  byProduct[idNonHigh==T, 'ExtremeBreakageProductOrSupplier'] = ifelse(byProduct[idNonHigh==T, 'BreakageDollars'] >= quantile(byProduct$BreakageDollars, .75), T, F)
  byProduct$SalesScaled = scale(log(byProduct$SalesDollars))
  byProduct$BreakageScaled = scale(log(byProduct$BreakageDollars))
  byProduct$BreakageCasesScaled = scale(log(byProduct$BreakageCases))
  productAttributes = df[(!duplicated(df$ProductId)), c('ProductId','ProductClass','Size','ProductType')]
  byProduct = merge(byProduct, productAttributes, on='ProductId', how='inner')
  return(byProduct)
}

byProduct = engineerFeatures(byProduct, df)


logNormalScale = function(x) scale(log(x))

summarizeReasonCodes = function(df, byProduct){
  byReason = aggregate(Breakage.Dollars ~ ReasonCode + ProductId, data=df, FUN=function(x) sum(x, na.rm=T))
  colnames(byReason)[colnames(byReason)=='Breakage.Dollars'] = 'BreakageDollars'
  byReason = tidyr::spread(byReason, ReasonCode, BreakageDollars)
  colnames(byReason) = gsub(' ', '', colnames(byReason))
  colnames(byReason) = gsub('-', '', colnames(byReason))
  byReason = zoo::na.fill(byReason, 0)
  byProduct = merge(byProduct, byReason, on='ProductId', how='inner')
  logCols = c('CrossDockBreakage','DriverBreakage','SupplierBreakage','WarehouseBreakage')
  for(col in logCols){
    noLogZero = byProduct[,col]>0
    newCol = paste0('Scaled',col)
    byProduct[noLogZero, newCol] = logNormalScale(byProduct[noLogZero, col])
    byProduct[, newCol] = zoo::na.fill(byProduct[, newCol], NA)
    byProduct[byProduct[,newCol]<-3, newCol] = NA
  }
  return(byProduct)
}

byProduct = summarizeReasonCodes(df, byProduct)

extractSignificantWarehouseProducts = function(byProduct){
  sumLinmod = summary(lm(ScaledWarehouseBreakage ~ SalesScaled + Product, data=byProduct))$coefficients
  dfCoefficients = data.frame(tScore=sumLinmod[sumLinmod[, 'Pr(>|t|)'] <= .10,'Pr(>|t|)'])
  significantCategories = rownames(dfCoefficients)
  significantCategories = significantCategories[significantCategories %!in% 'SalesScaled']
  significantCategories = gsub('Product','',significantCategories)
  return(significantCategories)
}

byProduct$WarehouseHighBreakageItem = extrWhseBrk = byProduct$Product %in% extractSignificantWarehouseProducts(byProduct)
byProduct$WarehouseHighBreakageItem = ifelse(extrWhseBrk & byProduct$ScaledWarehouseBreakage < 0.5, FALSE, extrWhseBrk)

extractSignificantDriverProducts = function(byProduct){
  sumLinmod = summary(lm(ScaledDriverBreakage ~ SalesScaled + Product, data=byProduct))$coefficients
  dfCoefficients = data.frame(tScore=sumLinmod[sumLinmod[, 'Pr(>|t|)'] <= .10,'Pr(>|t|)'])
  significantCategories = rownames(dfCoefficients)
  significantCategories = significantCategories[significantCategories %!in% 'SalesScaled']
  significantCategories = gsub('Product','',significantCategories)
  return(significantCategories)
}

byProduct$DriverHighBreakageItem = extrDrvBrk = byProduct$Product %in% extractSignificantDriverProducts(byProduct)
byProduct$DriverHighBreakageItem = ifelse(extrDrvBrk & byProduct$ScaledDriverBreakage < 0, FALSE, extrDrvBrk)

byWarehouse = function(df, byProduct){
  byWhse = aggregate(Breakage.Dollars ~ Warehouse + Product, data=df, FUN=function(x) sum(x, na.rm=TRUE))
  colnames(byWhse)[colnames(byWhse)=='Breakage.Dollars'] = 'BreakageDollars'
  byWhse = tidyr::spread(byWhse, Warehouse, BreakageDollars)
  colnames(byWhse) = gsub(' ', '', colnames(byWhse))
  byProduct = merge(byProduct, byWhse, on='ProductId', how='inner')
  logCols = c('KansasCity','SaintLouis')
  byProduct[, logCols] = zoo::na.fill(byProduct[, logCols], 0)
  for(col in logCols){
    noLogZero = byProduct[,col]>0
    newCol = paste0('Scaled',col)
    byProduct[noLogZero, newCol] = logNormalScale(byProduct[noLogZero, col])
    byProduct[, newCol] = zoo::na.fill(byProduct[, newCol], NA)
    byProduct[byProduct[,newCol]<-3, newCol] = NA
  }
  return(byProduct)
}

byProduct = byWarehouse(df, byProduct)

univariateLinearModel = function(linModel, X){
  intercept = linModel$coefficients[1]
  coef1 = linModel$coefficients[2]
  yPredict = intercept + X*coef1
  return(yPredict)
}

## ID products that are in both houses
missingKc = is.na(byProduct$ScaledKansasCity)
missingStl = is.na(byProduct$ScaledSaintLouis)
productInOneNotOther = missingKc | missingStl

## STL Breakage predicting KC Breakage
linModel = lm(ScaledKansasCity ~ ScaledSaintLouis, data=byProduct)
byProduct[!productInOneNotOther, 'GivenSTLPredictedKC'] = univariateLinearModel(linModel, byProduct[!productInOneNotOther, 'ScaledSaintLouis'])
byProduct[!productInOneNotOther, 'ErrorWarehousePredictionStlPredictKc'] = (byProduct[!productInOneNotOther, 'GivenSTLPredictedKC']+5) - (byProduct[!productInOneNotOther, 'ScaledKansasCity']+5)
byProduct[!productInOneNotOther, 'SquaredErrorWarehousePredictionStlPredictKc'] = byProduct[!productInOneNotOther, 'ErrorWarehousePredictionStlPredictKc']^2
byProduct[!productInOneNotOther, 'RootSquaredErrorWarehousePredictionStlPredictKc'] = sqrt(byProduct[!productInOneNotOther, 'SquaredErrorWarehousePredictionStlPredictKc'])

## KC Breakage predicting STL Breakage
linModel = lm(ScaledSaintLouis ~ ScaledKansasCity, data=byProduct)
byProduct[!productInOneNotOther, 'GivenKCPredictedSTL'] = univariateLinearModel(linModel, byProduct[!productInOneNotOther, 'ScaledKansasCity'])
byProduct[!productInOneNotOther, 'ErrorWarehousePredictionKcPredictStl'] = (byProduct[!productInOneNotOther, 'GivenKCPredictedSTL']+5) - (byProduct[!productInOneNotOther, 'ScaledSaintLouis']+5)
byProduct[!productInOneNotOther, 'SquaredErrorWarehousePredictionKcPredictStl'] = byProduct[!productInOneNotOther, 'ErrorWarehousePredictionKcPredictStl']^2
byProduct[!productInOneNotOther, 'RootSquaredErrorWarehousePredictionKcPredictStl'] = sqrt(byProduct[!productInOneNotOther, 'SquaredErrorWarehousePredictionKcPredictStl'])

## Mark High Breakage bn Houses
cutoff = 1.0
highBreakComparedToKc = byProduct[!productInOneNotOther, 'ErrorWarehousePredictionStlPredictKc'] >= cutoff
lowBreakComparedToKc = byProduct[!productInOneNotOther, 'ErrorWarehousePredictionStlPredictKc'] <= -cutoff

highBreakComparedToStl = byProduct[!productInOneNotOther, 'ErrorWarehousePredictionKcPredictStl'] >= cutoff
lowBreakComparedToStl = byProduct[!productInOneNotOther, 'ErrorWarehousePredictionKcPredictStl'] <= -cutoff

byProduct[!productInOneNotOther, 'ExtremeStlBreakageItem'] = extremeStl = highBreakComparedToKc | lowBreakComparedToKc
byProduct[!productInOneNotOther, 'ExtremeKcBreakageItem'] = extremeKc = highBreakComparedToStl | lowBreakComparedToStl
byProduct[!productInOneNotOther, 'DisproportionateBreakageBnHouses'] = extremeStl | extremeKc
byProduct$STLvsKCBreakage = paste0(byProduct$ExtremeKcBreakageItem, ' - ', byProduct$ExtremeStlBreakageItem)



#avgError = mean(byProduct$ErrorWarehousePredictionStlPredictKc, na.rm=T)
#sdError = sd(byProduct$ErrorWarehousePredictionStlPredictKc, na.rm=T)


plt3 = ggplot(data=byProduct, 
             aes(x=ScaledSaintLouis, y=ScaledKansasCity, label=ProductSummary)) +
  geom_point(aes(colour=DisproportionateBreakageBnHouses), 
             alpha=0.4) +
  theme_minimal() +
  theme(legend.position='none') +
  geom_line(data=byProduct, aes(y=ScaledKansasCity, x=GivenKCPredictedSTL),
            colour='black') +
  geom_line(data=byProduct, aes(x=ScaledSaintLouis, y=GivenSTLPredictedKC),
            colour='black') +
  labs(title='Breakage Between Warehouses', 
       y='$ Kansas City Breakage (scaled log-normal)', 
       x='$ Saint Louis Breakage (scaled log-normal)') +
  scale_x_continuous(limits=c(-3,3)) +
  scale_y_continuous(limits=c(-3,3))
ggplotly(plt3, width=9, height=9)
plt3

head(byProduct)
```

# Warehouse Breakage

Below displays the relationship between sales volume and warehouse breakage.

Using a custom algorithm that iterates over our products using a series of simple linear regression tests, products are identified as "High Warehouse Breakage" when they are statistically higher than products with similar sales. This is a simple, yet explanatory model (R-Squared ~)

The alpha used is 10% significance, which is somewhat more liberal than 5%. This means we'll have a few false positives as a cost while having more true positives as a benefit.

You'll note the variables lie between -3 and 3. This is for computational purposes only, and the scaling is not important for drawing conclusions. Scaling is a necessary step in machine learning to adjust for differences in orders of magnitude and underlying statistical distribution, and serves to maximize the effectiveness of a given algorithm. For those interested, both breakage and sales follow a log-normal distribution w.r.t. products, and were scaled accordingly.

This plot does not take into account differences in warehouse breakage between Kansas City & Saint Louis.

Each point represents a product. Hover your mouse over the points on the plot to see more information about the product in question.


```{r warehouseBreakagePlot}
plt1 = ggplot(data=byProduct[byProduct$ScaledWarehouseBreakage >= -3, ], 
             aes(x=SalesScaled, y=ScaledWarehouseBreakage, label=ProductSummary)) +
  geom_point(aes(colour=WarehouseHighBreakageItem, size=WarehouseBreakage), 
             alpha=0.4) +
  theme_minimal() +
  theme(legend.position='none') +
  geom_smooth(method='lm', se=F, aes(group=WarehouseHighBreakageItem), 
              colour='black', size=.5) +
  labs(title='Warehouse Breakage vs. Sales', 
       x='$ Sales (scaled log-normal)', 
       y='$ Warehouse Breakage (scaled log-normal)')
#ggplotly(plt1, width=9, height=9)
plt1
```

# Driver Breakage

The same principles stated above about Warehouse Breakage hold true for driver breakage. 

```{r driverBreakagePlot}
plt2 = ggplot(data=byProduct, 
             aes(x=SalesScaled, y=ScaledDriverBreakage, label=ProductSummary)) +
  geom_point(aes(colour=DriverHighBreakageItem, size=DriverBreakage), 
             alpha=0.4) +
  theme_minimal() +
  theme(legend.position='none') +
  geom_smooth(method='lm', se=F, aes(group=DriverHighBreakageItem), 
              colour='black', size=.5) +
  labs(title='Driver Breakage vs. Sales', 
       x='$ Sales (scaled log-normal)', 
       y='$ Driver Breakage (scaled log-normal)')
#ggplotly(plt2, width=9, height=9)
plt2
# linModel = lm(ScaledWarehouseBreakage ~ SalesScaled + WarehouseHighBreakageItem, data=byProduct)
# summary(linModel)
```

























