---
title: "<b>Roadnet Implementation</b>"
subtitle: "<b><small>Project Finalization</small></b>"
# author: "<small>Paul Washburn & Rick Ade</small>"
date: "<small>August 2016</small>"
output: revealjs::revealjs_presentation#html_document #ioslides_presentation #slidy_presentation #beamer_presentation #revealjs::revealjs_presentation #pdf_document
theme: solarized
center: true
fig_width: 10
fig_height: 5
fig_caption: true
widescreen: true
# navigation: slide
transition: slide
# background_transition: concave
# width: 1500
# height: 1200
autosize: true
---

```{r setup, include=FALSE}
library(RODBC)
library(dplyr)
library(ggplot2)
library(scales)
library(RColorBrewer)
library(ggthemes)
library(reshape2)
library(plotly)
library(plan)
library(plotrix)
library(xlsx)
library(htmlTable)

#get data for gantt
event = read.xlsx(file='C:/Users/pmwash/Desktop/Roadnet Implementation/Data/Planning Data/master_planning_roadnet.xlsx',
                  sheetName='events', header=TRUE)
events = c('TODAY') #event$label#
events_dates = c(as.character(Sys.Date())) #event$date#
tasks = read.xlsx(file='C:/Users/pmwash/Desktop/Roadnet Implementation/Data/Planning Data/master_planning_roadnet.xlsx',
                  sheetName='nodes_w_types', header=TRUE)
tasks = filter(tasks, type == 'Task', finished==0)


# make function for task lists
make_list = function(player, role) {
  Player = player
  Role = role
  task_matrix = data.frame(cbind(Player, Role))
  htmlTable(task_matrix)
}
```






# <b>Upcoming Tasks</b> <br><small>We are almost done! Let's finish strong!<br><br>It is vital that we maintain attention to detail moving forward, ensuring the tool is used to its fullest potential.<br><br>Thank you to the entire team for your hard work and patience throughout the process</small> {data-background=#BAC8D5}



## Active Tasks
<ul> 
  <li>Document statewide routing SOP</li>
  <li>Document data maintenance SOP</li>
  <li>Clean up & standardize RNA data</li>
  <li>Plan to phase-in dynamic routing</li>
  <li>Procure 2 widescreen monitors for routers</li>
  <li>Input truck weight limits/lengths/costs/names</li>
  <li>Finalize number of routes; contract</li>
  <li>Setup reverse API back from Roadnet</li>
  <li>ID and add new fields in AS400</li>
</ul>



## Active Tasks (Cont.)
<ul> 
  <li><s>Review/validate account service times</s></li>
  <li>Input chain prioritization mechanism</li>
  <li>New Daily Report template/data types</li>
  <li>Get blank driver sheet to each house</li>
  <li>Input DOT information to Roadnet</li>
  <li>Analyze dynamic parameters/optimize</li>
  <li>Decide on KPIs - centralize data</li>
</ul>



## Document Statewide Routing SOP <br><small><b>Due by August 30th</b></small>
```{r task0, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p0 = c('Joe Luna', 'Bob Kloeppinger', 'Paul Washburn')
r0 = c('Responsible', 'Responsible', 'Accountable')

make_list(player=p0, role=r0)
```
<p><b>Deliverable:</b> Document high level steps. Flesh out micro steps. Account for if/else contingencies. Distill into SOP. Test/perfect. Share SOP w/ group; group approves. Distribute.</p>
  


## Build RNA to AS400 API <br><small><b>Due by August 29th</b></small>
```{r task1, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p1 = c('Kevin Gagen', 'Paul Washburn')
r1 = c('Responsible', 'Accountable')

make_list(player=p1, role=r1)
```
<p><b>Deliverable:</b> Buildout reverse connectivity from Roadnet to AS400.</p>



## Document Data Maintenace SOP <br><small><b>Due by August 31st</b></small>
```{r task2, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p2 = c('Joe Luna', 'Bob Kloeppinger', 'Paul Washburn', 'Rick Ade')
r2 = c('Responsible', 'Responsible', 'Accountable', 'Accountable')

make_list(player=p2, role=r2)
```
<p><b>Deliverable:</b> Identify which data fields need maintenance. Define frequency for each. Decide who will be consulted and who will input data. Configure validation mechanism. Document. Test. Publish and distribute.</p>



## Clean/Standardize RNA Data <br><small><b>Due by August 31st</b></small>
```{r task3, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p3 = c('Joe Luna', 'Bob Kloeppinger', 'Tony Perri', 'Rich Stewart', 'Paul Washburn', 'Rick Ade')
r3 = c('Responsible', 'Responsible', 'Responsible', 'Responsible', 'Accountable', 'Accountable')

make_list(player=p3, role=r3)
```
<p><b>Deliverable:</b> Identify inaccuracies and fix. Standardize nomenclature. Input missing data.</p>



## Dynamic Phase-In Plan <br><small><b>Due by September 5th</b></small>
```{r task4, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p4 = c('Joe Luna', 'Tony Perri', 'Rick Ade')
r4 = c('Responsible', 'Responsible', 'Responsible')

make_list(player=p4, role=r4)
```
<p><b>Deliverable:</b> Develop detailed plan for phasing in dynamic routing complete with timeline and regions. Test/improve/finalize. Document. Communicate to Operations/Sales/Merchandising. </p>




## Procure 24" Widescreens (3 Sets) <br><small><b>Due by August 31st</b></small>
```{r task5, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p5 = c('Bill Schwein', 'Rick Ade', 'Paul Washburn')
r5 = c('Responsible', 'Responsible', 'Responsible')

make_list(player=p5, role=r5)
```
<p><b>Deliverable:</b> Routers need two 24" widescreens due to the extreme visual noise on the RNA screens. Procure. Distribute to routers in STL/KC/Springfield. </p>
  
  


## Input Truck/Employee Information <br><small><b>Due by August 31st</b></small>
```{r task6, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p6 = c('Paul Cunningham', 'Joe Luna', 'Rich Stewart','Tony Perri', 'Rick Ade')
r6 = c('Responsible', 'Responsible', 'Responsible', 'Responsible', 'Accountable')

make_list(player=p6, role=r6)
```
<p><b>Deliverable:</b> Input fixed/variable cost of trucks. Input Employee pay/OT rates. Input DOT information where applicable for trucks/employees. </p>






## Finalize Number of Routes <br><small><b>Due by August 31st</b></small>
```{r task7, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p7 = c('Paul Washburn', 'Rick Ade', 'Joe Luna', 'Paul Cunningham','Tony Perri', 'Rich Stewart')
r7 = c('Responsible', 'Responsible', 'Accountable', 'Accountable', 'Accountable', 'Accountable')

make_list(player=p7, role=r7)
```
<p><b>Deliverable:</b> Gather 2015 Daily Report data & derive probability of going over X routes for 10 days out of a rolling 30. Compare to intuitions of team. Describe objective data to team. Discuss; form consensus. Get SteerCo approval. Quote/sign contract. </p>







## Prioritize Chains/Strict Windows <br><small><b>Due by August 31st</b></small>
```{r task8, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p8 = c('Paul Washburn', 'Rick Ade', 'Randy Simpson', 'Don Hercher', 'Steve Jeunger', 'Tom West')
r8 = c('Responsible', 'Responsible', 'Accountable', 'Accountable', 'Consulted', 'Consulted')

make_list(player=p8, role=r8)
```
<p><b>Deliverable:</b> Identify prioritization mechanism for chains and strict time windows. Consult stakeholders. Test. Finalize/Approve/Implement. </p>







## Daily Report Template/Data Types <br><small><b>Due by August 31st</b></small>
```{r task9, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p9 = c('Paul Washburn', 'Rick Ade', 'Randy Simpson', 'Bob Kloeppinger')
r9 = c('Responsible', 'Responsible', 'Accountable', 'Accountable')

make_list(player=p9, role=r9)
```
<p><b>Deliverable:</b> Modify/standardize template for Daily Report. Establish data types for each column. Document. Add columns for cost/reload/etc. Standardize categories (names/trucks) via VLOOKUP. Agree on time-to-input-data expectations. Test. Implement. </p>







## Blank Driver Collection Sheet <br><small><b>Due by August 31st</b></small>
```{r task10, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p10 = c('Paul Washburn')
r10 = c('Responsible')

make_list(player=p10, role=r10)
```
<p><b>Deliverable:</b> Adapt the driver data collection sheet used previously for future use. Distribute template to each house. Print copies for each driver. Distribute. Use for new customers.  </p>







## Decide on DOT Data <br><small><b>Due by September 10th</b></small>
```{r task11, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p11 = c('Don Hercher', 'Randy Simpson', 'Rick Ade')
r11 = c('Responsible', 'Responsible', 'Responsible')

make_list(player=p11, role=r11)
```
<p><b>Deliverable:</b> Decide which DOT data (if any) to track in Roadnet for ease of access if a DOT audit should come up. Identify specific fields. Gather info. Input. Integrate to Maintenace SOP.  </p>









## Decide Routing KPIs <br><small><b>Due by August 31st</b></small>
```{r task12, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p12 = c('Don Hercher', 'Randy Simpson', 'Rick Ade', 'Paul Washburn')
r12 = c('Responsible', 'Responsible', 'Responsible', 'Responsible')

make_list(player=p12, role=r12)
```
<p><b>Deliverable:</b> Brainstorm potential KPIs. Develop reports to track. Assess their viability. Establish baseline.  </p>












## Experiment w/ Dynamic Parameters <br><small><b>Due by September 31st</b></small>
```{r task13, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p13 = c('Paul Washburn')
r13 = c('Responsible')

make_list(player=p13, role=r13)
```
<p><b>Deliverable:</b> Use sandbox and/or live routing to experiment with dynamic parameters. Track input parameters and outputs for cost/miles/hours etc. Perform statistical analysis to see optimal parameters. Find optimal settings for parameters and whether or not they differ by house. </p>
















# <b>Risk Assessment & Mitigation</b> <small>Following is an overview of project risks & their potential impacts. It is the team's resonsibility to mitigate risks by whatever reasonable means available. <br><br>If you see a risk to the project that is not displayed please raise your concern.</small> {data-background=#BAC8D5}



## Risk Matrix

```{r risks, echo=FALSE, fig.align='center', fig.width=8}
risks = read.xlsx(file='C:/Users/pmwash/Desktop/Roadnet Implementation/Data/Planning Data/master_planning_roadnet.xlsx',
                  sheetName='risks', header=TRUE)
nRow <- 5
nCol <- 5
m3 <- matrix(c(2,2,3,3,3,1,2,2,3,3,1,1,2,2,3,1,1,2,2,2,1,1,1,1,2), nrow = 5, ncol = 5, byrow = TRUE)
myData <- m3 
rownames(myData) <- c("5", "4", "3", "2", "1")  
colnames(myData) <- c("1", "2", "3", "4", "5")  
long_data = melt(myData)
colnames(long_data) <- c("Likelihood", "Consequence", "value")
long_data = mutate(long_data, value = Consequence + Likelihood)
r = risks
names(r) = c('risk', 'Likelihood', 'Consequence', 'mitigation', 'value')
# myPalette = colorRampPalette(rev(brewer.pal(5, "RdYlGn")))
myPalette = colorRampPalette(c('green', 'yellow', 'red', 'darkred'))

g = ggplot(data=long_data, aes(x=Consequence, y=Likelihood, fill=value))
base_plot = g + geom_tile() +
  scale_fill_gradientn(colours = myPalette(3)) + 
  scale_x_continuous(breaks = 0:6, expand = c(0, 0)) +
  scale_y_continuous(breaks = 0:6, expand = c(0, 0)) +
  coord_fixed() +
  theme_bw() +
  theme(legend.position='none')

final_plot = base_plot + 
  geom_point(data=r, position='jitter', size=r$Consequence, 
             aes(x=r$Consequence, y=r$Likelihood)) + 
  geom_text(data=r, position='jitter', size=3, label=r$risk, 
            aes(x=r$Consequence, y=r$Likelihood)) +
  ggtitle('Risk Matrix')

print(final_plot)
```








# <b>Moving Forward</b> <br><small>As we finish the project we will need to start turning our attention towards dynamic routing implementation.<br><br>This will be an ongoing process<br><br>We will also want to establish transparent reporting procedures on relevant KPIs.<br><br>This isn't the end of Roadnet -- it is the beginning. It will only be as good as we make it.</small> {data-background=#BAC8D5}


## Upcoming Key Decisions
<ul> 
  <li>Decide whether to put Samples etc in RN</li>
  <li>Decide & approve plan for phasing in dynamic routing</li>
  <li>Decide how many routes to contract</li>
  <li>Decide how to pre-empt driver relationships</li>
</ul>


## Next Steps
<ul> 
  <li>Finalize Routing SOP</li>
  <li>Finalize data maintenance SOP</li>
  <li>Clean up data at all houses in RNA</li>
  <li>Finalize dynamic phase-in plan</li>
  <li>Crystallize dynamic parameters that work</li>
  <li>Procure 24" widescreens for STL/SPFD/KC</li>
  <li>Input missing data in RNA</li>
  <li>Build reverse API back to AS400</li>
  <li>Distribute blank data collection sheets to Drivers</li>
  <li>Decide if DOT data needs tracking in RN</li>
  <li>Review requests for potential del. day changes</li>
  <li>Decide on KPIs/institute new Routing Report</li>
</ul>
  


# <b>Questions, Comments & Discussion</b> <br><small>Please take this time to clarify understanding, raise concerns, or provide input on the project's progress.<br><br>Thank you for your time!</small> {data-background=#BAC8D5}

# <b>Parting Words of Wisdom from Robert Schiller</b> <br><small>It amazes me how people are often more willing to act based on little or no data than to use data that is a challenge to assemble.</small> {data-background=#BAC8D5}





















