---
title: "<b>Roadnet Software Implementation</b>"
subtitle: "<b><small>Team Update & Next Steps</small></b>"
# author: "<small>Paul Washburn & Rick Ade</small>"
date: "<small>July 2016</small>"
output: revealjs::revealjs_presentation#html_document #ioslides_presentation #slidy_presentation #beamer_presentation #revealjs::revealjs_presentation #pdf_document
theme: solarized
center: true
fig_width: 10
fig_height: 5
fig_caption: true
widescreen: true
# navigation: slide
transition: slide
# background_transition: concave
# width: 1500
# height: 1200
autosize: true
---

```{r setup, include=FALSE}
library(RODBC)
library(dplyr)
library(ggplot2)
library(scales)
library(RColorBrewer)
library(ggthemes)
library(reshape2)
library(plotly)
library(plan)
library(plotrix)
library(xlsx)
library(htmlTable)

#get data for gantt
event = read.xlsx(file='C:/Users/pmwash/Desktop/Roadnet Implementation/Data/Planning Data/master_planning_roadnet.xlsx',
                  sheetName='events', header=TRUE)
events = c('TODAY') #event$label#
events_dates = c(as.character(Sys.Date())) #event$date#
tasks = read.xlsx(file='C:/Users/pmwash/Desktop/Roadnet Implementation/Data/Planning Data/master_planning_roadnet.xlsx',
                  sheetName='nodes_w_types', header=TRUE)
tasks = filter(tasks, type == 'Task', finished==0)


# make function for task lists
make_list = function(player, role) {
  Player = player
  Role = role
  task_matrix = data.frame(cbind(Player, Role))
  htmlTable(task_matrix)
}
```


<!-- # <b>How to Navigate</b> <br><small>Use your keyboard's arrows.<br><br>Right & Left arrows will bring you to the next section in the slideshow.<br><br>Up and down arrows will navigate to the next slide within a section.<br><br>Press "o" to see an outline of the presentation all at once.</small> {data-background=#99ff99} -->



<!-- # <b>Project Status</b> <br><small>Router training in STL has been completed; KC will have theirs next week.<br><br>Several "details" issues have arisen in this process.<br><br>The organization is looking at us -- and we are well poised to deliver positive results.<br><br>We are in the final stretch!</small> {data-background=#99ff99} -->


<!-- # <b>Progress Report</b> <br><small>Project is about 55% complete.<br><br>Staying on track is imperative to successful implementation this calendar year.<br><br>It is up to each of us to adhere to the schedule.</small> {data-background=#99ff99} -->

<!-- ## Detailed Project Timeline -->
<!-- ```{r timeline, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=12, fig.height=7.5} -->
<!-- create_gantt = function(key, desc, start, end, done, events, event_dates){ -->
<!--   roadnet_planner = as.gantt(key=key, description=desc, -->
<!--                              start=start, end=end, done=done)  -->

<!--   x = plot(roadnet_planner, -->
<!--            event.label=events, -->
<!--            event.time=events_dates, -->
<!--            time.lines.by="5 days", -->
<!--            main='Major Tasks Remaining in Roadnet', -->
<!--            col.done='green', -->
<!--            col.notdone='gray', -->
<!--            cex=1) -->

<!--   suppressWarnings(print(x)) -->
<!-- } -->


<!-- x = create_gantt(key=tasks$key, desc=tasks$label, start=tasks$start, -->
<!--              end=tasks$end, done=tasks$done, events=events, event_dates=event_dates) -->
<!-- suppressWarnings(print(x)) -->
<!-- ``` -->


<!-- ## Accomplishments -->
<!-- <ul>  -->
<!--   <li>Customer lockout SOP has been implemented</li> -->
<!--   <li>Saint Louis Router Training completed</li> -->
<!--   <li>Disaster Recovery plan outlined</li> -->
<!--   <li>API connections have been (mostly) built</li> -->
<!--   <li>Base routes have been (mostly) created</li> -->
<!--   <li></li> -->
<!-- </ul> -->





# <b>Upcoming Tasks</b> <br><small>The task list has grown; please review the timeline carefully.<br><br>Efforts on tasks will be self-directed based on who is involved with the sub-group responsible to complete. Please note who you will be working with on each task and plan/communicate accordingly.<br><br></small> {data-background=#99ff99}



## Active Tasks
<ul> 
  <li>Document statewide routing SOP</li>
  <li>Document data maintenance SOP</li>
  <li>Clean up & standardize RNA data</li>
  <li>Plan to phase-in dynamic routing</li>
  <li>Procure 2 widescreen monitors for routers</li>
  <li>Input truck weight limits/lengths/costs/names</li>
  <li>Finalize number of routes; contract</li>
  <li>Setup reverse API back from Roadnet</li>
  <li>ID and add new fields in AS400</li>
</ul>



## Active Tasks (Cont.)
<ul> 
  <li><s>Review/validate account service times</s></li>
  <li>Input chain prioritization mechanism</li>
  <li>New Daily Report template/data types</li>
  <li>Get blank driver sheet to each house</li>
  <li>Input DOT information to Roadnet</li>
  <li>Address new delivery days from Sales</li>
  <li>Decide on KPIs - centralize data</li>
  <li>Program Hogan driver cost to RNA</li>
</ul>



## Document Statewide Routing SOP <br><small><b>Due by August 30th</b></small>
```{r task0, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p0 = c('Joe Luna', 'Bob Kloeppinger', 'Paul Washburn')
r0 = c('Responsible', 'Responsible', 'Accountable')

make_list(player=p0, role=r0)
```
<p><b>Deliverable:</b> Document high level steps. Flesh out micro steps. Account for if/else contingencies. Distill into SOP. Test/perfect. Share SOP w/ group; group approves. Distribute.</p>
  


## Finalize RNA -> AS400 API <br><small><b>Due by August 29th</b></small>
```{r task1, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p1 = c('Kevin Gagen', 'Paul Washburn')
r1 = c('Responsible', 'Accountable')

make_list(player=p1, role=r1)
```
<p><b>Deliverable:</b> Buildout reverse connectivity from Roadnet to AS400.</p>



## Document Data Maintenace SOP <br><small><b>Due by August 31st</b></small>
```{r task2, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p2 = c('Joe Luna', 'Bob Kloeppinger', 'Paul Washburn')
r2 = c('Responsible', 'Responsible', 'Accountable')

make_list(player=p2, role=r2)
```
<p><b>Deliverable:</b> Identify which data fields need maintenance. Define frequency for each. Decide who will be consulted and who will input data. Configure validation mechanism. Document. Test. Publish and distribute.</p>



## Clean/Standardize RNA Data <br><small><b>Due by August 31st</b></small>
```{r task3, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p3 = c('Joe Luna', 'Bob Kloeppinger', 'Tony Perri', 'Rich Stewart', 'Paul Washburn', 'Rick Ade')
r3 = c('Responsible', 'Responsible', 'Responsible', 'Responsible', 'Accountable', 'Accountable')

make_list(player=p3, role=r3)
```
<p><b>Deliverable:</b> Identify inaccuracies and fix. Standardize nomenclature. Input missing data.</p>



## Dynamic Phase-In Plan <br><small><b>Due by September 5th</b></small>
```{r task4, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p4 = c('Joe Luna', 'Tony Perri', 'Rick Ade')
r4 = c('Responsible', 'Responsible', 'Responsible')

make_list(player=p4, role=r4)
```
<p><b>Deliverable:</b> Develop detailed plan for phasing in dynamic routing complete with timeline and regions. Test/improve/finalize. Document. Communicate to Operations/Sales/Merchandising. </p>




## Procure 24" Widescreens (3 Sets) <br><small><b>Due by August 31st</b></small>
```{r task5, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=7, fig.height=3}
p5 = c('Bill Schwein', 'Rick Ade', 'Paul Washburn')
r5 = c('Responsible', 'Responsible', 'Responsible')

make_list(player=p5, role=r5)
```
<p><b>Deliverable:</b> Routers need two 24" widescreens due to the extreme visual noise on the RNA screens. </p>
  
  










# <b>Risk Assessment & Mitigation</b> <small>Following is an overview of project risks & their potential impacts. It is the team's resonsibility to mitigate risks by whatever reasonable means available. <br><br>If you see a risk to the project that is not displayed please raise your concern.</small> {data-background=#99ff99}



## Risk Matrix

```{r risks, echo=FALSE, fig.align='center', fig.width=8}
risks = read.xlsx(file='C:/Users/pmwash/Desktop/Roadnet Implementation/Data/Planning Data/master_planning_roadnet.xlsx',
                  sheetName='risks', header=TRUE)
nRow <- 5
nCol <- 5
m3 <- matrix(c(2,2,3,3,3,1,2,2,3,3,1,1,2,2,3,1,1,2,2,2,1,1,1,1,2), nrow = 5, ncol = 5, byrow = TRUE)
myData <- m3 
rownames(myData) <- c("5", "4", "3", "2", "1")  
colnames(myData) <- c("1", "2", "3", "4", "5")  
long_data = melt(myData)
colnames(long_data) <- c("Likelihood", "Consequence", "value")
long_data = mutate(long_data, value = Consequence + Likelihood)
r = risks
names(r) = c('risk', 'Likelihood', 'Consequence', 'mitigation', 'value')
# myPalette = colorRampPalette(rev(brewer.pal(5, "RdYlGn")))
myPalette = colorRampPalette(c('green', 'yellow', 'red', 'darkred'))

g = ggplot(data=long_data, aes(x=Consequence, y=Likelihood, fill=value))
base_plot = g + geom_tile() +
  scale_fill_gradientn(colours = myPalette(3)) + 
  scale_x_continuous(breaks = 0:6, expand = c(0, 0)) +
  scale_y_continuous(breaks = 0:6, expand = c(0, 0)) +
  coord_fixed() +
  theme_bw() +
  theme(legend.position='none')

final_plot = base_plot + 
  geom_point(data=r, position='jitter', size=r$Consequence, 
             aes(x=r$Consequence, y=r$Likelihood)) + 
  geom_text(data=r, position='jitter', size=3, label=r$risk, 
            aes(x=r$Consequence, y=r$Likelihood)) +
  ggtitle('Risk Matrix')

print(final_plot)
```







# <b>Team Performance</b> <br><small>The Roadnet Team has performed well to-date. <br><br>Going forward, timely task completion will be absolutely vital.<br><br>Optimism towards project goal is important and doubts should be raised & addressed.<br><br>Empirical research on Project Management has been reviewed to help maintain adequate productivity and overall effectiveness.</small>{data-background=#99ff99}


## Factors of Team Effectiveness <small>There are 5 key factors that determine a team's effectiveness. <br>See study overview by clicking <a href="https://rework.withgoogle.com/blog/five-keys-to-a-successful-google-team/">"Do Managers Matter?"</a></small>
<ul>
  <li><b>Psychological Safety -</b>Opportunity to speak up & be heard</li>
  <li><b>Dependability -</b> Work completed on-time w/ excellence</li>
  <li><b>Structure & Clarity -</b> Clear roles, plans & goals</li>
  <li><b>Meaning -</b> Personal importance to the mission</li>
  <li><b>Impact -</b> Believing work matters & influences change</li>
</ul>



## Factors of Team Effectiveness
```{r factors_effectiveness, echo=FALSE, fig.align='center', fig.width=8}
roles = read.xlsx(file='C:/Users/pmwash/Desktop/Roadnet Implementation/Data/Planning Data/master_planning_roadnet.xlsx',
                  sheetName='roles', header=TRUE)
roles$role = factor(roles$role, levels=roles$role)
roles$score = as.numeric(roles$score)
g = ggplot(data=roles, aes(x=role, y=score))
g = g + geom_bar(stat='identity', fill='blue', colour='orange', size=2, alpha=0.6) +
  labs(title='Roadnet Team Score on Factors of Effectiveness', 
       x='Factor', y='Score') +
  theme_minimal() 
print(g)
```



## Factors of Team Effectiveness <small>Please raise any concerns you have about any of these categories. The goal is to complete this project with optimism, pride & excellence. If something is standing in your way it is important to shine a light on it.</small>
<ul>
  <li><b>Psychological Safety -</b> Speak up!</li>
  <li><b>Dependability -</b> Get quality work done on time!</li>
  <li><b>Structure & Clarity -</b> Is your role clear?</li>
  <li><b>Meaning -</b> Does project have meaning? Why/why not?</li>
  <li><b>Impact -</b> Influence organizational change!</li>
</ul>



<!-- ## Group Roles <br><small>We actively seek to cultivate these constructive roles</small> -->
<!-- <ul> -->
<!--   <li><b>Encourager -</b> Offers praise & acknowledges contributions</li> -->
<!--   <li><b>Harmonizer -</b> Reduces tension & promotes reconciliation</li> -->
<!--   <li><b>Compromizer -</b> In conflict scenario offers middleground</li> -->
<!--   <li><b>Gate Keeper -</b> Encourages participation & communication</li> -->
<!--   <li><b>Standard Setter -</b> Evaluates progress to standards</li> -->
<!-- </ul> -->



<!-- ## Task Roles <small>These roles are important to ask execution</small> -->
<!-- <ul> -->
<!--   <li>Initiator</li> -->
<!--   <li>Information Seeker</li> -->
<!--   <li>Opinion Seeker</li> -->
<!--   <li>Information Giver</li> -->
<!--   <li>Opinion Giver</li> -->
<!--   <li>Coordinator</li> -->
<!--   <li>Elaborator</li> -->
<!--   <li>Orientor</li> -->
<!--   <li>Evaluator</li> -->
<!--   <li>Procedure Technician</li> -->
<!--   <li>Recorder</l> -->
<!-- </ul> -->




# <b>Moving Forward</b> <br><small>As stated earlier, the project has kicked into high gear. <br><br>We will go from 40% to 80% complete much faster than we went from 0% to 40% complete.<br><br>The meat of the work will be performed in the next two months, and mistakes will not be immediately evident (if ever). Since the quality feedback loop is delayed we must ensure that seemingly small decisions are not made by taking the path of least resistance.<br><br>This period will be most important to success.</small> {data-background=#99ff99}


## Upcoming Key Decisions
<ul> 
  <li>Decide where data will live on permanent basis</li>
  <li>Decide & approve plan for phasing in dynamic routing</li>
  <li>Decide & approve ROI tracking plan</li>
  <li>Decide & approve keg routing process</li>
  <li>Decide & approve disaster recovery plan</li>
  <li>Decide whether to use staging database</li>
  <li>Decide if SQL or flat file for staging database</li>
  <li>Decide whether to send orders througout day; format</li>
  <li>Decide whether multiple routing sessions necessary</li>
  <li>Decide on HR data permissions for tracking ROI</li>
  <li>Decide what incentive structures to implement</li>
</ul>


## Next Steps
<ul> 
  <li>Build data bridges between AS400 & Roadnet Cloud</li>
  <li>Build reports relevant to routing; improve/automate</li>
  <li>Derive fields necessary for dynamic routing; automate</li>
  <li>Merge in missing data RNA database</li>
  <li>Formalize ROI tracking process</li>
  <li>Begin testing keg routing process in KC; document</li>
  <li>Routers will continue online training</li>
  <li>Develop disaster recovery plan</li>
  <li>SOPs: routing, maintenance, kegs, off-day, under $150</li>
  <li>Finalize ROI measurement strategy</li>
  <li>Outline all rules necessary for dynamic routing</li>
  <li>Develop plan for phasing in dynamic routing; consensus</li>
</ul>
  


# <b>Questions, Comments & Discussion</b> <br><small>Please take this time to clarify understanding, raise concerns, or provide input on the project's progress.<br><br>Thank you for your time!</small> {data-background=#99ff99}

# <b>Parting Words of Wisdom from Peter Drucker</b> <br><small>Management is doing things right; Leadership is doing the right things.<br><br>Plans are only good intentions unless they immediately degenerate into hard work.<br><br>The only thing we know about the future is that it will be different.<br><br>The best way to predict the future is to create it.</small> {data-background=#99ff99}





















