---
title: "<b><h1>Roadnet Dynamic Routing</h1></b>"
subtitle: "<b><small>Steering Committee Update</small></b>"
author: "<small>Paul Washburn & Rick Ade</small>"
date: "<small>January 25, 2016</small>"
output: revealjs::revealjs_presentation#html_document #ioslides_presentation #slidy_presentation #beamer_presentation #revealjs::revealjs_presentation
theme: solarized
center: true
fig_width: 10
fig_height: 5
fig_caption: true
widescreen: true
transition: slide
autosize: true
---

```{r setup, include=FALSE}
source('C:/Users/pmwash/Desktop/Project Management Tool/Project_Mgmt_Homebase/helper.R')
library(googleVis)
library(dplyr)
library(reshape2)
library(ggplot2)
library(plotly)
library(DT)

path = 'C:/Users/pmwash/Desktop/Project Management Tool/Project Data/Project Management Database.accdb'#driver = 'Driver={Microsoft Access Driver (*.mdb, *.accdb)};DBQ='
DB = odbcConnectAccess2007(path)

## Project List to choose from
PROJECTS = sqlFetch(DB, sqtable='Projects')



## Prep first tab for Timeline gantt chart
EMPS = sqlFetch(DB, sqtable='Employees')
TASK = sqlFetch(DB, sqtable='Tasks')
TASK = TASK %>% filter(Cancelled != 1)

print('Get Task List and merge it with Employees')
the_task = TASK$`Task Short`
the_responsible = strsplit(as.character(TASK$`Responsible (R)`), ';')
MASTER_TASKLIST = data.frame(Task=rep(the_task, sapply(the_responsible, length)), Responsible=unlist(the_responsible))
MASTER_TASKLIST = merge(EMPS[,c('EmployeeID','Full Name')], MASTER_TASKLIST, by.x='EmployeeID', by.y='Responsible')
MASTER_TASKLIST$EmployeeID = NULL
tasklist_fields = c('Task Short','Start Date','End Date','Planned Completion','Value')
MASTER_TASKLIST = merge(MASTER_TASKLIST, TASK[,tasklist_fields], by.x='Task', by.y='Task Short')
rm(the_task, the_responsible)

MASTER_TASKLIST$`Start Date` = as.Date(MASTER_TASKLIST$`Start Date`, '%Y-%m-%d')
MASTER_TASKLIST$`End Date` = as.Date(MASTER_TASKLIST$`End Date`, '%Y-%m-%d')
MASTER_TASKLIST$`Planned Completion` = as.Date(MASTER_TASKLIST$`Planned Completion`, '%Y-%m-%d')


MASTER_TASKLIST = MASTER_TASKLIST %>% arrange(`Planned Completion`, `Start Date`)

options = list(timeline="{groupByRowLabel:true, colorByRowLabel:true}",
               backgroundColor='#ffd', 
               height=1000, width=1300)
TIMELINE_PLOT = gvisTimeline(data=MASTER_TASKLIST,
                        rowlabel = 'Task',
                        barlabel = 'Full Name',
                        start = 'Start Date',
                        end = 'Planned Completion',
                        options=options)
#plot(TIMELINE_PLOT)



## Project List to choose from
RISKS = sqlFetch(DB, sqtable='Risks')
RISKS = RISKS %>% arrange(desc(Value))

generate_risk_matrix = function(RISKS) {
  myData = matrix(c(2,2,3,3,3,1,2,2,3,3,1,1,2,2,3,1,1,2,2,2,1,1,1,1,2), 
              nrow = 5, 
              ncol = 5, 
              byrow = TRUE)
  rownames(myData) = c("5", "4", "3", "2", "1")
  colnames(myData) = c("1", "2", "3", "4", "5")  
  long_data = melt(myData)
  colnames(long_data) = c("Likelihood", "Consequence", "Value")
  
  long_data = mutate(long_data, Value = Consequence + Likelihood)
  
  r = RISKS[,c('Risk','Probability','Impact','Mitigation','Value')]
  
  myPalette = colorRampPalette(c('green', 'yellow', 'red', 'darkred'))
  
  g = ggplot(data=long_data, aes(x=Consequence, y=Likelihood, fill=Value))
  base_plot = g + geom_tile() +
    scale_fill_gradientn(colours = myPalette(3)) + 
    scale_x_continuous(breaks = 0:6, expand = c(0, 0)) +
    scale_y_continuous(breaks = 0:6, expand = c(0, 0)) +
    coord_fixed() +
    theme_bw() +
    theme(legend.position='none')
  
  final_plot = base_plot + 
    geom_point(data=r, position='jitter', 
               aes(x=Impact, y=Probability, size=Value)) + 
    geom_text(data=r, position='jitter', size=3, 
              aes(x=Impact, y=Probability, label=Risk)) 
  
  #final_plot = ggplotly(final_plot)
  
  return(final_plot)
}

RISK_PLOT = generate_risk_matrix(RISKS)



## Get decision points

DECISIONS = sqlFetch(DB, sqtable='Decisions')
DECISION_TABLE = DECISIONS[,c('Decision', 'Importance')] %>% arrange(desc(Importance))

lst = c(as.list(DECISIONS$`Decision Maker`))
str(lst)



# Better more clear gantt chart

TASK = TASK %>% arrange(`Planned Completion`, `Start Date`)
TASK$Sequence = 1:length(TASK$ID)

create_gantt = function(key, desc, start, end, done, neededBy){
  roadnet_planner = as.gantt(key=key, description=desc,
                             start=start, end=end, done=done) #, # done) #, NeededBy) #, done, neededBy)
  
  GANTT = plot(roadnet_planner,
           event.label='Today',
           event.time=as.character(Sys.Date()),
           time.lines.by="1 week",
           main='Major Tasks Remaining in Roadnet',
           col.done='green',
           col.notdone='gray',
           cex=1)
  
  print(GANTT)
}

#png('N:/2016 MB Projects/Roadnet/Planning/timeline.png', width = 1200, height = 800)



## Get task list
library(tidyr)
# add objective to this dataframe
TASK_TABLE = aggregate(`Full Name` ~ Task + `Planned Completion`, data=MASTER_TASKLIST, FUN=paste0)
TASK_TABLE = data.frame(TASK_TABLE) 
TASK_TABLE = TASK_TABLE[desc(TASK_TABLE$Planned.Completion) ,]
names(TASK_TABLE) = c('Task','Planned Completion','Team Members')



## Get objective list
OBJECTIVES = sqlFetch(DB, sqtable='Objectives')
METRICS = sqlFetch(DB, sqtable='Metrics')
M = METRICS[,c('ID','Metric')]
METRICS = METRICS[,c('Metric','Importance')] %>% arrange(desc(Importance))
the_objective = OBJECTIVES$`Objective`
the_metrics = strsplit(as.character(OBJECTIVES$`Metrics`), ';')
MASTER_OBJECTIVES = data.frame(Objective=rep(the_objective, sapply(the_metrics, length)), `Metrics`=unlist(the_metrics))
MASTER_OBJECTIVES = merge(MASTER_OBJECTIVES, M, by.x='Metrics', by.y='ID')
MASTER_OBJECTIVES = aggregate(Metric ~ Objective, data=MASTER_OBJECTIVES, FUN=paste0)

odbcCloseAll()
```


# <b>Executive Summary</b> <br><small>Dynamic implentation has started full-swing after a planning period.<br><br>Much time being spent on people management stemming from changes in plans regarding reporting; certain member is expressing extreme dissastisfaction and unwillingness to do work under current self-imposed constraints on the team.<br><br>Experimentation has begun for dynamic testing; however RN is limited in its modeling capabilities. May require sooner/longer live testing on certain routes.</small> {data-background-iframe="http://www.cs.usyd.edu.au/~shhong/PPI.jpg"}

## Immediate Attention
- Decision on whether to purchase more route licenses
- Tolerance for missed time windows - tradeoff for ROI
- Truck drivers start time - currently highly variable
- Unwillingness to perform tasks within team
- What a plan for Sales/Merchandising should address
- Plan meeting w/ Sales & Merchandising: who/when/where
- Merchandising Plan - mechanisms of coordination
- Grapevine talk of double-inputting Daily Report - risks
- Preference for case definition: want to reflect reality

## Operations Update
- Dynamic experimentation underway, choosing test routes
- 2-5 test routes per house; near one another; urban
- Gathering data on different methods of dynamic routing
- Limited experimentation capability in RN 
- May need to start live testing sooner, longer on test rtes.
- Consolidating proposed plan for sales/merchandising
- Consolidating proposed plan for drivers/customers
- After ID'ing experimental routes will begin live tests

## IT Update
- IT/Finance have been brokered; vetting fields
- IT decided GP$ will be extracted from AS400, not sent
- SQL location for routing data built & awaiting DR
- Next step is to merge RN data w/ Daily Report
- Simple report has been outlined for IT per MG request
- Getting pushback on this; desire prototype; PW refused
- Grievance about getting assigned out of the blue
- Originally task assigned to PW until told not to do it
- "I will not do this unless you provide a prototype" - told no
- "I will not do this w/o a data dictionary" - provided already
- Loudly in office "This is the worst project I've ever been on"

## Decisions
```{r decisions, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=10, fig.height=6}
div(datatable(DECISION_TABLE), style='font-size:50%')
```

# <b>Tasks & Timeline</b> <br><small></small> {data-background-iframe="http://www.cs.usyd.edu.au/~shhong/PPI.jpg"}

## Timeline
```{r timeline_details, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=11, fig.height=7}
create_gantt(key=TASK$Sequence, desc=TASK$`Task Short`, start=TASK$`Start Date`,
                                             end=TASK$`Planned Completion`, done=(TASK$Done*100))
```

## Task List
```{r tasklist, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=6, fig.height=6}
library(DT)
div(datatable(TASK_TABLE), style='font-size:50%')
```

# <b>Risks, Objectives, Metrics</b> <br><small></small> {data-background-iframe="http://www.cs.usyd.edu.au/~shhong/PPI.jpg"}

## Risk Matrix
```{r risk_matrix, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=10, fig.height=6}
ggplotly(RISK_PLOT)
```

## Risks
```{r risk_table, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=10, fig.height=6}
div(datatable(RISKS[, c('Risk','Mitigation','Value')]), style='font-size:50%')
```

## Objectives
```{r objectives, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=10, fig.height=6}
div(datatable(MASTER_OBJECTIVES), style='font-size:50%')
```

## Metrics
```{r metrics, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=10, fig.height=6}
div(datatable(METRICS[,c('Metric','Importance')]), style='font-size:50%')
```

# <b>Moving Forward</b> <br><small></small> {data-background-iframe="http://www.cs.usyd.edu.au/~shhong/PPI.jpg"}

## Next Steps
- Decide how strict we will make time windows
- Decide if we will get more licenses
- Decide plan for minimizing impact to customers
- Decide plan for coordinating w/ Merchandising
- Decide whether driver start time will change
- Outline/document plan for Sales/Merchandising
- Schedule meeting with Sales/Merchandising
- Resolve issue with report buildout
- Experiment with selected live routes
- Crystallize dynamic routing SOP
- Meet w/ Sales & provide detailed plan; Gain approval
- Communicate w/ drivers all relevant info


## <b>Questions? Comments?</b> <br><small></small> {data-background-iframe="http://www.cs.usyd.edu.au/~shhong/PPI.jpg"}


## <b>Parting Words of Wisdom from W. Edwards Deming</b> <br><small>"It is not necessary to change. Survival is not mandatory."<br><br>"In God we trust. All else bring data."<br><br>"Quality is everyone's responsibility."</small> {data-background-iframe="http://www.cs.usyd.edu.au/~shhong/PPI.jpg"}





















