---
title: "<b>Roadnet Routing Solution</b>"
subtitle: "<b><small>Steering Committee Update</small></b>"
author: "<small>Paul Washburn & Rick Ade</small>"
date: "<small>July 7, 2016</small>"
output: revealjs::revealjs_presentation#html_document #ioslides_presentation #slidy_presentation #beamer_presentation #revealjs::revealjs_presentation
theme: solarized
center: true
fig_width: 10
fig_height: 5
fig_caption: true
widescreen: true
# navigation: slide
transition: rotate
# width: 1500
# height: 1200
autosize: true
---

```{r setup, include=FALSE}
library(RODBC)
library(dplyr)
library(ggplot2)
library(scales)
library(RColorBrewer)
library(ggthemes)
library(reshape2)
library(plotly)
library(plan)
library(plotrix)
library(xlsx)





#get data for gantt
event = read.xlsx(file='C:/Users/pmwash/Desktop/Roadnet Implementation/Data/Planning Data/master_planning_roadnet.xlsx',
                  sheetName='events', header=TRUE)
events = c('TODAY') #event$label#
events_dates = c(as.character(Sys.Date())) #event$date#
tasks = read.xlsx(file='C:/Users/pmwash/Desktop/Roadnet Implementation/Data/Planning Data/master_planning_roadnet.xlsx',
                  sheetName='nodes_w_types', header=TRUE)
tasks = filter(tasks, type == 'Task')

```



# <b>Progress Report</b> {data-background=#A4A4A4}

## Detailed Project Timeline
```{r timeline, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, fig.width=12, fig.height=7.5}
create_gantt = function(key, desc, start, end, done, events, event_dates){
  roadnet_planner = as.gantt(key=key, description=desc,
                             start=start, end=end, done=done) #, # done) #, NeededBy) #, done, neededBy)

  x = plot(roadnet_planner,
           event.label=events,
           event.time=events_dates,
           time.lines.by="5 days",
           main='Major Tasks Remaining in Roadnet',
           col.done='green',
           col.notdone='gray',
           cex=1)

  suppressWarnings(print(x))
}

#png('N:/2016 MB Projects/Roadnet/Planning/timeline.png', width = 1200, height = 800)
x = create_gantt(key=tasks$key, desc=tasks$label, start=tasks$start,
             end=tasks$end, done=tasks$done, events=events, event_dates=event_dates)
suppressWarnings(print(x))
```


## Accomplishments
<ul> 
  <li>All requisite data has been collected by drivers</li>
  <li>All requisite data has been input into digital form</li>
  <li>Derivative data has been identified for transformation</li>
  <li>RTS database has been converted to RNA database</li>
  <li>Data supply chain has been outlined for entire system</li>
  <li>Processes have been outlined at high level</li>
  <li>Reporting requirements have been gathered</li>
  <li>IT team has met with & trained on API connectivity</li>
  <li>Service times have been inferred statistically outside KC</li>
</ul>


## Challenges & Unresolved Issues
<p><center>Maximizing dynamic routing is the largest challenge and will be central to the project. Other unresolved issues include:</p></center>
<ul> 
  <li>Need resolution to AS400 lockout during routing</li>
  <li>Need to develop Keg Routing process in Roadnet</li>
  <li>Need detailed specificationss for IT team</li>
  <li>Need to decide on SQL or flat file staging database</li>
  <li>Need to decide if Azure for staging database</li>
  <li>Need to decide time cutoff: orders & input</li>
  <li>Need to decide if we send orders throughout day</li>
  <li>Need to derive fields that do not exist for routing</li>
</ul>


## Next Steps
<ul> 
  <li>Decide where data will live on permanent basis</li>
  <li>Build data bridges between AS400 & Roadnet Cloud</li>
  <li>Build reports relevant to routing; improve/automate</li>
  <li>Merge in dynamic routing data into RNA database</li>
  <li>Formalize ROI tracking process & tool; get approval</li>
  <li>Begin testing keg routing process in KC; document</li>
  <li>Routers will continue online training</li>
  <li>Disaster recovery SOP will be developed & approved</li>
  <li>SOPs: routing, maintenance, kegs, off-day, under $150</li>
  <li>Finalize ROI measurement strategy</li>
  <li>Outline all rules necessary for dynamic routing</li>
  <li>Develop plan for phasing in dynamic routing; consensus</li>
</ul>
  
  
  
  

# <b>Risk Assessment & Mitigation</b> {data-background=#A4A4A4}
<small><b>Overview of potential challenges in perspective of their potential impacts</small></b>


## Risk Matrix

```{r risks, echo=FALSE, fig.align='center', fig.width=8}
risks = read.xlsx(file='C:/Users/pmwash/Desktop/Roadnet Implementation/Data/Planning Data/master_planning_roadnet.xlsx',
                  sheetName='risks', header=TRUE)
nRow <- 5
nCol <- 5
m3 <- matrix(c(2,2,3,3,3,1,2,2,3,3,1,1,2,2,3,1,1,2,2,2,1,1,1,1,2), nrow = 5, ncol = 5, byrow = TRUE)
myData <- m3 
rownames(myData) <- c("5", "4", "3", "2", "1")  
colnames(myData) <- c("1", "2", "3", "4", "5")  
long_data = melt(myData)
colnames(long_data) <- c("Likelihood", "Consequence", "value")
long_data = mutate(long_data, value = Consequence + Likelihood)
r = risks
names(r) = c('risk', 'Likelihood', 'Consequence', 'mitigation', 'value')
# myPalette = colorRampPalette(rev(brewer.pal(5, "RdYlGn")))
myPalette = colorRampPalette(c('green', 'yellow', 'red', 'darkred'))

g = ggplot(data=long_data, aes(x=Consequence, y=Likelihood, fill=value))
base_plot = g + geom_tile() +
  scale_fill_gradientn(colours = myPalette(3)) + 
  scale_x_continuous(breaks = 0:6, expand = c(0, 0)) +
  scale_y_continuous(breaks = 0:6, expand = c(0, 0)) +
  coord_fixed() +
  theme_bw() +
  theme(legend.position='none')

final_plot = base_plot + 
  geom_point(data=r, position='jitter', size=r$Consequence, 
             aes(x=r$Consequence, y=r$Likelihood)) + 
  geom_text(data=r, position='jitter', size=3, label=r$risk, 
            aes(x=r$Consequence, y=r$Likelihood)) +
  ggtitle('Risk Matrix')

print(final_plot)
```





## Overview of Risk Items
<ul> 
  <li><b>Complex Rules:</b> Challenging to implement</li>
  <li><b>Consultants:</b> Communication has been challenging</li>
  <li><b>Keg Routing:</b> Model needs be conceived & developed</li>
  <li><b>Habit Changes:</b> Habits will be sticky for routers and drivers</li>
  <li><b>Reports:</b> Reporting difficult hard to reverse engineer</li>
  <li><b>Dynamic routing phase-in:</b> Plan incremental phase-in</li>
  <li><b>IT Training:</b> C# .NET and XML for API connectivity</li>
  <li><b>Sales & Cust. Service:</b> Data/cut-offs/under $150/off days</li>
  <li><b>Driver Cooperation:</b> Order of route; custom asks of router</li>
</ul>


## Risk Mitigation <small>Implementing Complex Rules for Dynamic Routing</small>
<ul> 
  <li>Dynamic routing requires excellent data maintenance</li>
  <li>Necessitates clear & concise communication w/ Omnitracs</li>
  <li>All needs of the system need to be outlined prior to on-site</li>
  <li>Will require testing of all possible scenarios</li>
  <li>We must plan for driver/customer personal relationships</li>
  <li>We must plan prioritizing certain customers over others</li>
</ul>


## Risk Mitigation  <small>Consultant Miscommunications & Errors</small>
<p>Somewhere between the sales process & our interaction with the consultants information has been lost on Omnitrac's side. 
Twice the issue has been addressed with Linda Harris, the project manager. The IT team is very helpful.</p>
<ul> 
  <li>Misunderstandings will be nipped in the bud immediately</li>
  <li>Open, honest & clear communication practices employed</li>
  <li>Technical items will be brought up to technical consultants</li>
</ul>


## Risk Mitigation  <small>Keg Routing Using Roadnet</small>
<p>Keg routing is currently done outside of Roadnet, and a workable process must be modeled, developed & tested.
Kansas City will be the laboratory for this testing.</p>
<ul> 
  <li>Need to develop a field that indicates "Is.Keg?" for product</li>
  <li>Keg delivery days need to be established for each client</li>
  <li>Keg route for new customers needs to have clear criteria</li>
</ul>

## Risk Mitigation <small>Operations, Sales, & Driver Habit Changes</small>
<p>The following must be addressed/pre-empted:</p>
<ul> 
  <li>Driver on-boarding process needs updating</li>
  <li>Customer & Route data maintenance SOP</li>
  <li>Data origination (Sales/Operations/Data Integrity) SOPs</li>
  <li>Drivers currently choose order of stops; need enforce order</li>
</ul>


## Risk Mitigation: <small>Re-Engineering Routing & Operations Reports</small>
<ul> 
  <li>Driver on-boarding process needs updating</li>
  <li>Customer & Route data maintenance SOP</li>
  <li>Data origination (Sales/Operations/Data Integrity) SOPs</li>
  <li>Drivers currently choose order of stops; need enforce order</li>
</ul>






# <b>Financial Assessment</b> <br><small>Initial ROI estimations assume 3% fuel savings & 2% labor savings.</small>{data-background=#A4A4A4}


## Horizon for ROI  
<p>harvardiana domensius comensius annum harvardiana domensius comensius annum harvardiana domensius comensius annum</p>


## Tenative Plan for Tracking ROI <small>This process will need to account for statistical fluctuations in fuel, labor & case production</small>





























