---
title: "<b>Major Brands Graphics Report</b>"
author: "Paul Washburn, Operations Analyst"
date: "May 2017"
output: 
  pdf_document:
      df_print: "kable" 
      fig_width: 10
      fig_height: 9
---

```{r setup, include=FALSE}
## VITAL -- MAKE SURE ALL CURRENT DESIGNERS ARE PRESENT BELOW
active_designers = c('Mueller, Rachel','Riehlman, Brittany','Wilhoit, Katie','Wright, Paige')

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)

## Graphics data dump from Diver
library(rpivotTable)
library(dplyr)
library(reshape2)
library(lubridate)
library(treemap)
library(ggplot2)
library(googleVis)
library(plotly)
library(stringr)
library(tidyr)
library(reshape2)
library(lubridate)
source('C:/Users/pmwash/Desktop/R_files/Data Input/Helper.R')

MONTHS = c('January','February','March','April','May','June',
           'July','August','September','October','November','December')
this_yr = round(as.numeric(format(Sys.Date(), '%Y')),0)
last_yr = round(as.numeric(format(Sys.Date(), '%Y')) - 1,0)
twoyrsago = round(as.numeric(format(Sys.Date(), '%Y')) - 2,0)

thismo_numeric = month(Sys.Date())
month_long = function(mo) month(mo, T, F)
ytd_months = unlist(lapply(seq(1, thismo_numeric, by=1), month_long))

pct_chg = function(new, old) {
  round(((new-old)/abs(old))*100, 1)
}

## Read in and clean up the data
df = read.csv('C:/Users/pmwash/Desktop/Re-Engineered Reports/Graphics/graphics_data_dump_diver.csv', header=TRUE)
df$POSTERJob.ID = factor(df$POSTERJob.ID)
df = df %>% filter(Year %in% c(last_yr, this_yr))
df$Invoice.Date = dat = strptime(df$Invoice.Date, '%m/%d/%Y')
df$Week = week(dat)
df$Month = month(dat, TRUE, FALSE)
df$ProjectID_LineID = paste0(df$POSTERJob.ID, '_', df$POSTER.Item.ID)
df$POSTER.REPRINT = df$POSTER.REPRINT == 'Y'

## Set rownames
rownames(df) = c(1:NROW(df))

## Test df
#df = df[1:1000, ]

## Get string for job status - parse for turnaround
job_status = as.character(df$POSTER.JOB.STATUS)
df$POSTER.JOB.STATUS = NULL
names(job_status) = df$POSTERJob.ID
job_status = strsplit(job_status, ',')

for(i in 1:length(job_status)){
  try({
    start = regmatches(job_status[[i]][1][1], gregexpr("(?=\\().*?(?<=\\))", job_status[[i]][1][1], perl=T))
    assgn = regmatches(job_status[[i]][2][1], gregexpr("(?=\\().*?(?<=\\))", job_status[[i]][2][1], perl=T))
    brand = regmatches(job_status[[i]][3][1], gregexpr("(?=\\().*?(?<=\\))", job_status[[i]][3][1], perl=T))
    costs = regmatches(job_status[[i]][4][1], gregexpr("(?=\\().*?(?<=\\))", job_status[[i]][4][1], perl=T))
    artsy = regmatches(job_status[[i]][5][1], gregexpr("(?=\\().*?(?<=\\))", job_status[[i]][5][1], perl=T))
    appro = regmatches(job_status[[i]][6][1], gregexpr("(?=\\().*?(?<=\\))", job_status[[i]][6][1], perl=T))
    cmplt = regmatches(job_status[[i]][7][1], gregexpr("(?=\\().*?(?<=\\))", job_status[[i]][7][1], perl=T))
    shipp = regmatches(job_status[[i]][8][1], gregexpr("(?=\\().*?(?<=\\))", job_status[[i]][8][1], perl=T))
    
    start = gsub("[()]", "", start)
    assgn = gsub("[()]", "", assgn)
    brand = gsub("[()]", "", brand)
    costs = gsub("[()]", "", costs)
    artsy = gsub("[()]", "", artsy)
    appro = gsub("[()]", "", appro)
    cmplt = gsub("[()]", "", cmplt)
    shipp = gsub("[()]", "", shipp)
    
    start = gsub("\\s+", " ", start)
    assgn = gsub("\\s+", " ", assgn)
    brand = gsub("\\s+", " ", brand)
    costs = gsub("\\s+", " ", costs)
    artsy = gsub("\\s+", " ", artsy)
    appro = gsub("\\s+", " ", appro)
    cmplt = gsub("\\s+", " ", cmplt)
    shipp = gsub("\\s+", " ", shipp)
    
    df[i, 'Kickoff'] = start
    df[i, 'ArtistAssigned'] = assgn
    df[i, 'ObtainBrandMentions'] = brand
    df[i, 'CostApproved'] = costs
    df[i, 'ArtworkComplete'] = artsy
    df[i, 'RequesterApproved']= appro
    df[i, 'JobComplete'] = cmplt
    df[i, 'JobShipped'] = shipp
  })
}

## Format as date for maths
munge_date = function(dat) format(strptime(dat, '%b %d %Y %I:%M%p'), '%Y-%m-%d %H:%M')  
dat_cols = c('Kickoff','ArtistAssigned','ObtainBrandMentions','CostApproved',
             'ArtworkComplete','RequesterApproved','JobComplete','JobShipped')
df[, dat_cols] = sapply(df[, dat_cols], munge_date)

## Obtain time spent in each category
df$Turnaround_KickoffToShip = round(difftime(df$JobShipped, df$Kickoff, units="days"), 1)
df$Stage1_KickoffToAssignment = round(difftime(df$ArtistAssigned, df$Kickoff, units="days"), 1)
df$Stage2_AssignmentToBrandMentions = round(difftime(df$ObtainBrandMentions, df$ArtistAssigned, units="days"), 1)
df$Stage3_BrandMentionsToCostApproval = round(difftime(df$CostApproved, df$ObtainBrandMentions, units="days"), 1)
df$Stage4_CostApprovalToArtworkComplete = round(difftime(df$ArtworkComplete, df$CostApproved,units="days"), 1)
df$Stage5_ArtworkCompleteToRequesterApproval = round(difftime(df$RequesterApproved, df$ArtworkComplete, units="days"), 1)
df$Stage6_RequesterApprovalToCompletion = round(difftime(df$JobComplete, df$RequesterApproved, units="days"), 1)
df$Stage7_CompletionToShip = round(difftime(df$JobShipped, df$JobComplete, units="days"), 1)

## Obtain time from kickoff til each stage
df$KickoffToArtistAssigned = round(difftime(df$ArtistAssigned, df$Kickoff, units="days"), 1)
df$KickoffToBrandMentions = round(difftime(df$ObtainBrandMentions, df$Kickoff, units="days"), 1)
df$KickoffToCostApproval = round(difftime(df$CostApproved, df$Kickoff, units="days"), 1)
df$KickoffToArtworkComplete = round(difftime(df$ArtworkComplete, df$Kickoff, units="days"), 1)
df$KickoffToRequesterApproval = round(difftime(df$RequesterApproved, df$Kickoff, units="days"), 1)
df$KickoffToArtworkComplete = round(difftime(df$ArtworkComplete, df$Kickoff, units="days"), 1)
df$KickoffToArtworkComplete = round(difftime(df$ArtworkComplete, df$Kickoff, units="days"), 1)

df$KickoffMonth = as.character(month(df$Kickoff, T, F))
df$InvoiceMonth = as.character(month(df$Invoice.Date, T, F))

df$KickoffYear = kick_yr = as.character(year(df$Kickoff))
df$InvoiceYear = invo_yr = as.character(year(df$Invoice.Date))

df$Profit = round(df$POSTER.Price - df$POSTER.CB.Total, 2)

# ## Write to CSV for Python
write.csv(df, 'C:/Users/pmwash/Desktop/Re-Engineered Reports/Graphics/intermediate_graphics_data_dump_diver.csv',
          row.names=FALSE)


## Get current months
this_month = as.character(month(Sys.Date(), T, F))
last_month = as.character(month(month(Sys.Date())-1, T, F))
beforethat = as.character(month(month(Sys.Date())-2, T, F))
last_3 = c(this_month, last_month, beforethat)

## Isolate this year and last year data only
df_thisyr_lastyr = df[(df$KickoffYear %in% c(this_yr, last_yr)) | 
                        (df$InvoiceYear %in% c(this_yr, last_yr)) & 
                        (df$POSTER.Designer %in% active_designers), ]

## Isolate YTD for this year and last year
invoiced_firstmos = (df_thisyr_lastyr$InvoiceMonth %in% ytd_months)
kickdoff_firstmos = (df_thisyr_lastyr$KickoffMonth %in% ytd_months)

df_ytd_thislast = df_thisyr_lastyr[invoiced_firstmos | kickdoff_firstmos, ]


## Isolate out last 3 mo from thisyr lastyr data
kickoff_month = df_thisyr_lastyr$KickoffMonth = as.character(month(df_thisyr_lastyr$Kickoff, T, F))
invoice_month = df_thisyr_lastyr$InvoiceMonth = as.character(month(df_thisyr_lastyr$Invoice.Date, T, F))

kickoff_year = df_thisyr_lastyr$KickoffYear = as.character(year(df_thisyr_lastyr$Kickoff))
invoice_year = df_thisyr_lastyr$InvoiceYear = as.character(year(df_thisyr_lastyr$Invoice.Date))


startmo = kickoff_month %in% last_3 
endinmo = invoice_month %in% last_3 

trailing_3 = df_thisyr_lastyr[startmo==T | endinmo==T, ]

df_thisyr = df[(df$KickoffYear == this_yr) | (df$InvoiceYear == this_yr) & (df$POSTER.Designer %in% active_designers), ]
```


# Measures of success for Graphics Team
This section was designed to help the Graphics department and management gain insight into the Graphics operation. In contrast, the next major section of this report is geared towards Graphics' impact on Sales and the organization at-large. Unless otherwise specified, the data considered is from all jobs submitted this year, and the data is accessed via a large dump from Diver of all fields and all dates available in the system.

## Turnaround by Designer
Figures below include weekends and holidays (i.e. holidays and weekends are not backed out of the duration calculations), and durations are measured in days. Active designers include Rachel, Brittany, Katie and Paige; all others are filtered out of the dataset. If this should not be the case please email Paul Washburn to change the filter criteria.


```{r turnaround}
turn_cols = cbind(df_thisyr$Turnaround_KickoffToShip, 
                  df_thisyr$KickoffToArtworkComplete, 
                  df_thisyr$Stage1_KickoffToAssignment,
                  df_thisyr$Stage2_AssignmentToBrandMentions,
                  df_thisyr$Stage3_BrandMentionsToCostApproval,
                  df_thisyr$Stage4_CostApprovalToArtworkComplete,
                  df_thisyr$Stage5_ArtworkCompleteToRequesterApproval,
                  df_thisyr$Stage6_RequesterApprovalToCompletion,
                  df_thisyr$Stage7_CompletionToShip)
turnaround = aggregate(turn_cols ~ df_thisyr$POSTER.Designer, FUN=function(x) round(mean(x, na.rm=T), 1))
names(turnaround) = c('X','Turnaround','Completion','Stage1','Stage2',
                      'Stage3','Stage4','Stage5','Stage6','Stage7')
rownames(turnaround) = turnaround$X
turnaround$X = NULL
turnaround
```


```{r descriptions}
guide_df = data.frame(row.names=c('Stage 1','Stage 2','Stage 3','Stage 4','Stage 5','Stage 6','Stage 7','Completion','Turnaround'),
                      Description=c('Job kickoff til artist assignment (days)',
                                    'Artist assignment til brand mentions obtained (days)',
                                    'Mentions obtained til cost approved (days)',
                                    'Cost approved til artwork complete (days)',
                                    'Artwork complete til requester approval (days)',
                                    'Requester approval til job completion (days)',
                                    'Job completion til ship (days)',
                                    'Job kickoff til job marked as complete (days)',
                                    'Job kickoff til job shipment (days)'))
guide_df
```


```{r turnaround_plot, fig.height=5, fig.width=9}
turnaround_x = data.frame(t(turnaround))
turnaround_x$Item = rownames(turnaround_x)
rownames(turnaround_x) = NULL
turnaround_x = melt(turnaround_x, 'Item')
turnaround_x$variable = gsub('\\..', ', ', turnaround_x$variable)

turns_df = turnaround_x[turnaround_x$Item %in% c('Completion','Turnaround'), ]
stage_df = turnaround_x[turnaround_x$Item %!in% c('Completion','Turnaround'), ]
stage_df$Item = factor(stage_df$Item, levels=c('Stage1','Stage2','Stage3','Stage4',
                                               'Stage5','Stage6','Stage7')) 

library(gridExtra)

ggplot(turns_df, aes(x=variable, y=value, group=Item)) +
  geom_bar(stat='identity', position='dodge', aes(fill=variable), colour='black') +
  facet_wrap(~Item, ncol=3, scales='free_y') +
  theme_minimal() +
  theme(axis.text.x=element_text(angle=90, hjust=1)) +
  labs(x='', y='Days', title='Average Turnaround & Completion (Days) by Designer')

ggplot(stage_df, aes(x=Item, y=value, group=variable)) +
  geom_bar(stat='identity', position='dodge', aes(fill=variable), colour='black') +
  #facet_wrap(~variable, ncol=3, scales='free_y') +
  theme_minimal() +
  theme(axis.text.x=element_text(angle=90, hjust=1)) +
  labs(x='', y='Days', title='Average Days in Each Stage by Designer')
```


## Total Price & Mentions by Designer

```{r price_mentions_plot}
## melt and isolate data by designer
val_cols = c('POSTER.Price','POSTER.MB.mentions')
id_cols = c('POSTER.Designer','Month')

bydesigner_melt = melt(df_thisyr, id_cols, val_cols)

bydesigner = aggregate(value ~ variable + POSTER.Designer + Month, data=bydesigner_melt, FUN=sum)
bydesigner = spread(bydesigner, 'Month', 'value')

l_dfs = split(bydesigner, bydesigner$variable)
price_df = l_dfs$POSTER.Price

library(scales)
byd_df = bydesigner
namz = names(byd_df)
namz = c(unlist(namz[namz %!in% c('variable','POSTER.Designer')]))
mentions_df_melt = melt(byd_df, c('variable','POSTER.Designer'), namz)
names(mentions_df_melt) = c('var','POSTER.Designer','Month','value')

ggplot(mentions_df_melt, aes(x=Month, y=value, group=POSTER.Designer)) +
  geom_line(aes(colour=POSTER.Designer)) +
  geom_point(alpha=0.6) +
  facet_wrap(~var, nrow=2, scales='free_y') +
  theme_minimal() +
  labs(title='Total Price and Mentions per Month by Designer', x='', y='') +
  scale_y_continuous(labels=comma)


process_df = function(df) {
  rownames(df) = df$POSTER.Designer
  df$POSTER.Designer = df$variable = NULL
  return(df)
}
```


## Cost by Designer

A monthly sum of Poster Price, shown by month.

```{r price_bydesigner, fig.height=7, fig.width=9}
process_df(price_df)
```

```{r costs_bydesigner_plot, fig.height=5, fig.width=9}
price_t = data.frame(t(process_df(price_df)))
names(price_t) = gsub('\\..', ', ', names(price_t))
price_t$Name = rownames(price_t)
rownames(price_t) = NULL
price_t_melt = melt(price_t, 'Name', active_designers)
price_t_melt$Name = factor(price_t_melt$Name, levels=MONTHS) 

ggplot(price_t_melt, aes(x=Name, y=value, group=variable)) +
  geom_bar(stat='identity', position='dodge', aes(fill=variable), colour='black') +
  facet_wrap(~variable, ncol=4) +
  theme_minimal() +
  theme(axis.text.x=element_text(angle=90, hjust=1)) +
  labs(x='', y='Dollars', title='Sum of Poster Price per Month by Designer') +
  scale_y_continuous(labels=dollar)
```


## Brand Mentions by Designer
Sum of all MB mentions by Designer for the current year, shown by month. 

```{r mentions_bydesigner}
mentions_df = l_dfs$POSTER.MB.mentions
process_df(mentions_df)
```

Total number of brand mentions by Designer YTD.
```{r rowsums}
ttments = data.frame(t(rowSums(process_df(mentions_df), na.rm=T)))
rownames(ttments) = 'Tot Brand Mentions YTD'
names(ttments) = gsub('\\..',', ',names(ttments))
ttments
```

Average number of brand mentions per month by Designer YTD.

```{r rowmns}
avgments = data.frame(t(rowMeans(process_df(mentions_df), na.rm=T)))
rownames(avgments) = 'Avg Brand Mentions per Month'
names(avgments) = gsub('\\..',', ',names(avgments))
avgments
```



```{r mentions_plot, fig.height=5, fig.width=9}
mentions_t = data.frame(t(process_df(mentions_df)))
names(mentions_t) = gsub('\\..', ', ', names(mentions_t))
mentions_t$Name = rownames(mentions_t)
rownames(mentions_t) = NULL
mentions_t_melt = melt(mentions_t, 'Name', active_designers)
mentions_t_melt$Name = factor(mentions_t_melt$Name, levels=MONTHS) 

ggplot(mentions_t_melt, aes(x=Name, y=value, group=variable)) +
  geom_bar(stat='identity', position='dodge', aes(fill=variable), colour='black') +
  facet_wrap(~variable, ncol=4) +
  theme_minimal() +
  theme(axis.text.x=element_text(angle=90, hjust=1)) +
  labs(x='', y='Number of Brand Mentions', title='Brand Mentions per Month by Designer')
```



## Reprints by Designer
Total number of reprints for the current year, by Designer. Percent of Total is shown as a percent; in other words, it has been multiplied by 100 (e.g. 1.2 indicates 1.2%, or 0.012). Reprints are counted at the Job ID level, meaning a job with 10 items marked as reprints will be counted one time. It is possible to add in reprints at the Job Item level if this information is desired.

```{r reprints}
reprint_cols = c('POSTERJob.ID','POSTER.Designer')
no_dupes = !duplicated(df[,reprint_cols])

reprints = df[no_dupes, c('POSTERJob.ID','POSTER.Designer','POSTER.REPRINT','Year')]
reprints = reprints[reprints$Year == this_yr, ]
reprints = aggregate(POSTER.REPRINT ~ POSTER.Designer, data=reprints, FUN=sum)

len_unique = function(x) length(unique(x))
tot_jobs = aggregate(POSTERJob.ID ~ POSTER.Designer, data=df_thisyr, FUN=len_unique)
reprints = merge(reprints, tot_jobs, by='POSTER.Designer', how='all')
reprints = process_df(reprints)

## Specify column names
names(reprints) = c('Number of Reprints', 'Total Jobs')
reprints$`Reprints as % of Total Jobs` = round((reprints$`Number of Reprints` / reprints$`Total Jobs`)*100, 1)
reprints
```

```{r reprint_plot, fig.height=5, fig.width=9}
reprints_t = data.frame(t(reprints))
names(reprints_t) = gsub('\\..', ', ', names(reprints_t))
reprints_t$Name = rownames(reprints_t)
rownames(reprints_t) = NULL
reprints_t_melt = melt(reprints_t, 'Name', active_designers)

ggplot(reprints_t_melt, aes(x=variable, y=value, group=Name)) +
  geom_bar(stat='identity', position='dodge', aes(fill=variable), colour='black') +
  facet_wrap(~Name, ncol=4, scales='free_y') +
  theme_minimal() +
  theme(axis.text.x=element_text(angle=90, hjust=1)) +
  labs(x='', y='')

```


## Number of Jobs per Month by Designer

Total number of jobs by designer, shown by month.

```{r jobspermo_bydesigner}
jobspermo = aggregate(POSTERJob.ID ~ POSTER.Designer + Month, data=df_thisyr, FUN=len_unique)
jobspermo = spread(jobspermo, 'Month', 'POSTERJob.ID')
jobspermo = process_df(jobspermo)
jobspermo
```

YTD total number of jobs by designer.

```{r totjobrowsums}
tottjobs = data.frame(t(rowSums(jobspermo, na.rm=T)))
rownames(tottjobs) = 'Tot Jobs  YTD'
names(tottjobs) = gsub('\\..',', ',names(tottjobs)) 
tottjobs
```

YTD average number of jobs per month by designer.

```{r meanjobrowmeans}
avgjobs = data.frame(t(rowMeans(jobspermo, na.rm=T)))
rownames(avgjobs) = 'Avg Jobs per Month'
names(avgjobs) = gsub('\\..',', ',names(avgjobs)) 
avgjobs
```



```{r, fig.height=5, fig.width=9}
t_jobs = data.frame(t(jobspermo))
t_jobs$Month = row.names(t_jobs)
rownames(t_jobs) = NULL
t_jobs = melt(t_jobs, 'Month', gsub(', ','..',active_designers))
t_jobs$variable = gsub('\\..', ', ', t_jobs$variable)
t_jobs$Month = factor(t_jobs$Month, levels=MONTHS)

ggplot(data=t_jobs, aes(x=Month, y=value, group=variable)) +
  geom_line(aes(colour=variable)) +
  geom_point(alpha=.6, size=1.5) +
  labs(x='Month', y='Number of Jobs', title='Number of Jobs by Designer') +
  theme_minimal()
```


## Pipeline & Carrying Costs by Designer

Summary of current jobs in the pipeline. Only jobs that have a Kickoff date yet do not have a Ship date are considered. 

```{r pipeline}
not_shipped = (is.na(df_thisyr$JobShipped)==T)
started = (is.na(df_thisyr$Kickoff)==F)

df_pipeline = df_thisyr[not_shipped & started, ]
pipeline_summary = aggregate(cbind(POSTERJob.ID, ProjectID_LineID) ~ POSTER.Designer,
                             data=df_pipeline, FUN=len_unique)
price_summary = aggregate(cbind(POSTER.Price, POSTER.MB.mentions) ~ POSTER.Designer,
                             data=df_pipeline, FUN=function(x) round(sum(x, na.rm=T), 0))
pipeline_summary = merge(pipeline_summary, price_summary, on='POSTER.Designer', how='all')


pipeline_summary = process_df(pipeline_summary)
names(pipeline_summary) = c('Current Jobs', 'Current Items', 'Total Price', 'Total Mentions')
pipeline_summary
```




## Future Metrics for Graphics Department
Currently two metrics that were requested are not available. 

  - On-Time completion of job: The field for Requested Finish Date in POSTer is unreliable as of now for various reasons. It defaults to 2 weeks, and is not always updated. If some sort of guidelines are issued to this regard then the field will need to be added to the main Dive from which this data is acquired (which is really just a massive dump).
  - Number of "rush" jobs: The "rush" field is not passed from POSTer to Diver in the raw model. When this field is passed to Diver the metric will be added.



<br><br><br><br><br>





# Measures of Success for Major Brands

This section was designed to provide Leadership succinct insights on Graphics impact on the wider organization. The goal is for this section to contain everything that has to do with Graphics, yet is not immediately relevant to managing the graphics team, workflow or personnel. 



## By Company

### YTD Number of Jobs by Company

Month below is defined as the Kickoff month, or the month in which the Job started.

```{r bylocation_bymo}
kickedoff_byhouse = aggregate(POSTERJob.ID ~ KickoffYear + Company, data=df_ytd_thislast, FUN=len_unique)
kickedoff_byhouse = kickedoff_byhouse[kickedoff_byhouse$KickoffYear != twoyrsago, ]
kickedoff_byhouse = spread(kickedoff_byhouse, 'KickoffYear', 'POSTERJob.ID')
rownames(kickedoff_byhouse) = kickedoff_byhouse$Company
kickedoff_byhouse$Company = NULL

kickedoff_byhouse$`Percent Change (%)` = pct_chg(kickedoff_byhouse[, as.character(this_yr)], kickedoff_byhouse[, as.character(last_yr)])
kickedoff_byhouse
```

### YTD Number of Jobs by Month

The data shown below includes records for this year and last year where *either the Kickoff date's month or the Invoice Date's month are the same as this month, last month, or the one before that.* For example, today is May 1st then the dataset below would show records for which either the Invoice or Kickoff month is May, April and March (this year and last). 

Year-to-date Jobs kicked off by Company, shown by year.

```{r bylocation_ytd_kickedoff}
kickedoff_byhouse = aggregate(POSTERJob.ID ~ KickoffYear + KickoffMonth + Company, 
                              data=df_ytd_thislast, FUN=len_unique)
kickedoff_byhouse = kickedoff_byhouse[kickedoff_byhouse$KickoffYear != twoyrsago & 
                                        kickedoff_byhouse$KickoffMonth %in% ytd_months, ]
kickedoff_byhouse = spread(kickedoff_byhouse, 'KickoffYear', 'POSTERJob.ID')
kickedoff_byhouse$`Percent Change (%)` = pct_chg(kickedoff_byhouse[, as.character(this_yr)], 
                                                 kickedoff_byhouse[, as.character(last_yr)])
kickedoff_byhouse$KickoffMonth = factor(kickedoff_byhouse$KickoffMonth, levels=ytd_months)
kickedoff_byhouse = kickedoff_byhouse[order(kickedoff_byhouse$KickoffMonth), ]

## Split dataframes by company
make_rownames = function(df, mocol) {
  rownames(df) = df[, mocol]
  df[, mocol] = NULL
  return(df)
}
kickedoff_byhouse = split(kickedoff_byhouse, kickedoff_byhouse$Company)
KC_kickoffs = make_rownames(kickedoff_byhouse$`KANSAS CITY`, 'KickoffMonth')
STL_kickoffs = make_rownames(kickedoff_byhouse$`ST LOUIS`, 'KickoffMonth')
MMO_kickoffs = make_rownames(kickedoff_byhouse$`MID MISSOURI`, 'KickoffMonth')

KC_kickoffs
STL_kickoffs
MMO_kickoffs
```

### YTD Graphics Profit by Company

Profit in the months so far this year (i.e. YTD months), year-over-year. Graphics Profit is defined as YTD Poster Price minus YTD Charge Back Price.

```{r ytd_pctprofit}
profit_byhouse = aggregate(Profit ~ KickoffYear + Company, data=df_ytd_thislast, FUN=function(x) round(sum(x, na.rm=T), 2))
profit_byhouse = profit_byhouse[profit_byhouse$KickoffYear != twoyrsago, ]
profit_byhouse = spread(profit_byhouse, 'KickoffYear', 'Profit')
rownames(profit_byhouse) = profit_byhouse$Company
profit_byhouse$Company = NULL

profit_byhouse$`Percent Change (%)` = pct_chg(profit_byhouse[, as.character(this_yr)], profit_byhouse[, as.character(last_yr)])
profit_byhouse
```





## By Customer Account

Top customer accounts *(by number of Graphics Jobs)* YTD, compared to the same period last year.

```{r jobs_byaccount}
NOT_REAL_CUSTOMERS = c('GENERAL MARKET ALL-STL','GENERAL MARKET ALL-MMS',
                       'GENERAL MARKET ALL-KC','GENERAL MARKET ALL-MMN','',
                       'MAJOR BRANDS INTERNAL-STL','GENERAL MARKET ON-PREMISE STL',
                       'MAJOR BRANDS INTERNAL-KC')

jobs_byaccount = aggregate(POSTERJob.ID ~ KickoffYear + Customer, data=df_ytd_thislast, FUN=len_unique)
jobs_byaccount = jobs_byaccount[jobs_byaccount$KickoffYear != twoyrsago, ]
jobs_byaccount = spread(jobs_byaccount, 'KickoffYear', 'POSTERJob.ID')
jobs_byaccount = jobs_byaccount[jobs_byaccount$Customer %!in% NOT_REAL_CUSTOMERS, ]
rownames(jobs_byaccount) = jobs_byaccount$Customer
jobs_byaccount$Customer = NULL

jobs_byaccount$`Percent Change (%)` = pct_chg(jobs_byaccount[, as.character(this_yr)], 
                                                 jobs_byaccount[, as.character(last_yr)])
jobs_byaccount = jobs_byaccount[order(jobs_byaccount$`2017`, decreasing=T), ]
head(jobs_byaccount, 50)
```

Top customer accounts *(by Graphics Profit)* YTD, compared to the same period last year.

```{r profit_byaccount}
profit_byaccount = aggregate(Profit ~ KickoffYear + Customer, data=df_ytd_thislast, FUN=function(x) round(sum(x, na.rm=T), 2))
profit_byaccount = profit_byaccount[profit_byaccount$KickoffYear != twoyrsago, ]
profit_byaccount = spread(profit_byaccount, 'KickoffYear', 'Profit')
profit_byaccount = profit_byaccount[profit_byaccount$Customer %!in% NOT_REAL_CUSTOMERS, ]
rownames(profit_byaccount) = profit_byaccount$Customer
profit_byaccount$Customer = NULL

profit_byaccount$`Percent Change (%)` = pct_chg(profit_byaccount[, as.character(this_yr)], 
                                                 profit_byaccount[, as.character(last_yr)])
profit_byaccount = profit_byaccount[order(profit_byaccount$`2017`, decreasing=T), ]
head(profit_byaccount, 50)
```





## By Supplier

Top suppliers *(by number of Graphics Jobs)* YTD, compared to the same period last year.

```{r jobs_bysupplier}
jobs_bysupplier = aggregate(POSTERJob.ID ~ KickoffYear + Supplier, data=df_ytd_thislast, FUN=len_unique)
jobs_bysupplier = jobs_bysupplier[jobs_bysupplier$KickoffYear != twoyrsago, ]
jobs_bysupplier = spread(jobs_bysupplier, 'KickoffYear', 'POSTERJob.ID')
jobs_bysupplier = jobs_bysupplier[jobs_bysupplier$Supplier != '', ]
rownames(jobs_bysupplier) = jobs_bysupplier$Supplier
jobs_bysupplier$Supplier = NULL

jobs_bysupplier$`Percent Change (%)` = pct_chg(jobs_bysupplier[, as.character(this_yr)], 
                                                 jobs_bysupplier[, as.character(last_yr)])
# jobs_bysupplier = jobs_bysupplier[jobs_bysupplier$`2017` != 0]
jobs_bysupplier = jobs_bysupplier[order(jobs_bysupplier$`2017`, decreasing=T), ]
head(jobs_bysupplier, 35)
```

Top suppliers *(by Graphics Profit)* YTD, compared to the same period last year.

```{r profit_bysupplier}
profit_bysupplier = aggregate(Profit ~ KickoffYear + Supplier, data=df_ytd_thislast, FUN=function(x) round(sum(x, na.rm=T), 2))
profit_bysupplier = profit_bysupplier[profit_bysupplier$KickoffYear != twoyrsago, ]
profit_bysupplier = spread(profit_bysupplier, 'KickoffYear', 'Profit')
profit_bysupplier = profit_bysupplier[profit_bysupplier$Supplier != '', ]
rownames(profit_bysupplier) = profit_bysupplier$Supplier
profit_bysupplier$Supplier = NULL

profit_bysupplier$`Percent Change (%)` = pct_chg(profit_bysupplier[, as.character(this_yr)], 
                                                 profit_bysupplier[, as.character(last_yr)])
# profit_bysupplier = profit_bysupplier[profit_bysupplier$`2017` != 0]
profit_bysupplier = profit_bysupplier[order(profit_bysupplier$`2017`, decreasing=T), ]
head(profit_bysupplier, 35)
```








## By Brand






## By Requester







# What's Working? What's Not?
















































## Logical Future Improvements
  - Instead of placing all brand mentions on one line in POSTer, store each mention as a separate line. This will create marginally more work for Graphics, yet will immensely improve the insights we will be able to gain into individual brands & suppliers. We can then use formal tests to see which Graphics products are working and which are not. 



















































<!-- ## Python to process -->
<!-- ```{python} -->
<!-- import pandas as pd -->

<!-- path = 'C:/Users/pmwash/Desktop/Re-Engineered Reports/Graphics/intermediate_graphics_data_dump_diver.csv' -->
<!-- df = pd.read_csv(path, header=0) -->
<!-- ## Use Python to process strings -->
<!-- df.head() -->
<!-- ``` -->






































