---
title: "<b><h1>Shipping Labor</h1></b>"
subtitle: "<b><small>Predictive Model for Budgeting</small></b>"
author: "<small>Paul M. Washburn - Operations Analyst</small>"
date: "<small>November 2016</small>"
output: revealjs::revealjs_presentation#html_document #ioslides_presentation #slidy_presentation #beamer_presentation #revealjs::revealjs_presentation
theme: solarized
center: true
fig_width: 10
fig_height: 5
fig_caption: true
widescreen: true
transition: slide
autosize: true
---

```{r setup, include=FALSE}

library(dplyr)
library(ggplot2)
library(scales)
library(caret)
library(plotly)
library(lubridate)
library(chron)
library(timeDate)
library(scatterplot3d)


start_date = ISOdate(year=2011, month=1, day=1, hour=0, min=0, sec=0)
end_date = ISOdate(year=2017, month=1, day=1, hour=0, min=0, sec=0)
date_vector = seq(start_date, end_date, by='1 day')
year_vector = year(date_vector)
wday_vector = wday(date_vector, label=TRUE, abbr=FALSE)
month_vector = month(date_vector, label=TRUE, abbr=FALSE)
holidays = as.Date(date_vector) %in% as.Date(holidayNYSE(year=c(2011:2016)))
weekend = is.weekend(date_vector)
selling_day = ifelse(weekend == FALSE & holidays == FALSE, TRUE, FALSE)

sell_days = data.frame(date_vector, year_vector, wday_vector, month_vector, weekend, holidays, selling_day)
names(sell_days) = c('Date', 'Year','Weekday','Month','Is.Weekend', 'Is.Holiday', 'Is.Selling.Day')

COUNT_SELLING_DAYS = aggregate(Is.Selling.Day ~ Month + Year, data=sell_days, FUN=sum)
names(COUNT_SELLING_DAYS) = c('Month','Year','Number.of.Sales.Days')


labor_model = 'C:/Users/pmwash/Desktop/Re-Engineered Reports/Projects/Shipping Labor Prediction Model/Labor Prediction Model Data.csv'

monthly_data_all = read.csv(labor_model, header=TRUE)
monthly_data = monthly_data_all %>% filter(Year %in% c(2015, 2016))

monthly_data = data.frame(monthly_data %>% group_by(Year, House) %>%
  mutate(Cumulative.Projections = cumsum(Sales.Projections),
         Cumulative.Sales = cumsum(Dollars.Sold)))
monthly_data$Month = factor(monthly_data$Month, levels=c('January','February','March','April','May','June',
                                     'July','August','September','October','November','December'))


monthly_data = merge(monthly_data, COUNT_SELLING_DAYS, by=c('Year','Month'), all.x=TRUE)

monthly_data$Over.Short.of.Projection = monthly_data$Dollars.Sold - monthly_data$Sales.Projections
monthly_data$Met.Sales.Goal = monthly_data$Over.Short.of.Projection >= 0



monthly_data_all = merge(monthly_data_all, COUNT_SELLING_DAYS, by=c('Year','Month'), all.x=TRUE)


##3 MONTH QTY DEMANDED MODEL OF STD CASES SOLD AS FN OF GP HOUSE AND PRODUCTION DAY S
three_mo_demand_model = lm(Std.Cases.Sold ~ Mark.Up + House + Production.Days, data=monthly_data_all)



M = monthly_data_all %>% filter(Production.Days < 21)

new_dat = data.frame(Mark.Up=M$Mark.Up, 
                     House=M$House, 
                     Production.Days=M$Production.Days)

M$Forecast.Demand.3.Mo = predict(three_mo_demand_model, new_dat, interval='p')
M$Error.Demand.3.Mo.Forecast = M$Std.Cases.Sold - M$Forecast.Demand.3.Mo[1] 


m = monthly_data

new_dat_m = data.frame(Mark.Up=m$Mark.Up, 
                     House=m$House, 
                     Production.Days=m$Production.Days)

m$Forecast.Demand.3.Mo = new_dat_m$Forecast.Demand.3.Mo = predict(three_mo_demand_model, new_dat_m, interval='p')
m$Error.Demand.3.Mo.Forecast = m$Std.Cases.Sold - m$Forecast.Demand.3.Mo[, 1] 



##PRODUCTION MODEL -- PREDICT CASES PRODUCED OFF OF DEMAND FORECAST
PRODUCTION_MODEL = lm(m$Cases.Delivered ~ m$Forecast.Demand.3.Mo[,1])
summary(PRODUCTION_MODEL)

new_dat_m_production = data.frame(Forecasted.Demand.3.Mo = m$Forecast.Demand.3.Mo[,1])

m$Forecast.Production = predict(PRODUCTION_MODEL, new_dat_m_production, interval='p')





##LABOR MODEL -- PREDICT LABOR HOURS PER MONTH OFF OF PRODUCTION FORECAST (WHICH COMES FROM DEMAND FORECAST)
LABOR_MODEL = lm(m$Night.Ship.Hours ~ m$Forecast.Production[,1] + m$House + m$Production.Days)
summary(LABOR_MODEL)
MSE_LABOR = sqrt(mean(LABOR_MODEL$residuals ^ 2))

new_dat_m_labor = data.frame(Forecast.Production=m$Forecast.Production[,1], 
                             House=m$House,
                             Production.Days=m$Production.Days)

m$Forecast.Ship.Hours = predict(LABOR_MODEL, new_dat_m_labor, interval='p')
m$Error.Forecast.Ship.Hours = m$Night.Ship.Hours - m$Forecast.Ship.Hours[,1]


#

# ############################################################ 12062016
# 
# summary(lm(Cumulative.Sales ~ Cumulative.Projections, data=df))
# plot(df$Cumulative.Projections, df$Cumulative.Sales)
# 
# ######## mess around check
# # NOTE projections for MMO split 54.4% for KC and 45.6% for STL
# x_model = lm(Dollars.Sold ~ Sales.Projections, data=monthly_data) # + Production.Days
# summary(x_model)
# 
# 
# 



```









# <b>Executive Summmary</b> <br><small>This analysis reviews monthly data from 2011-2016 with the goal of finding a predictive model for total monthly night shipping hours.<br><br>Two demand models - for different time horizons - were developed in order to serve as input to the labor model. Demand, or Sales, is then translated into Cases Produced via the same methodology.<br><br>Each of the 4 predictive models were developed based only on what can be observed ahead of time.</small> {data-background=#e6e6e6}

## <b>Executive Summary</b> <br><small>All models are highly predictive.<br><br>The flow of predictions was tested in the context of historical data, and results appear to hold well at both warehouses.<br><br>The prediction flow follows:<br>DEMAND => PRODUCTION => SHIP HOURS<br><br>As always with machine leraning it is important to test the assumptions of these models over time, including conducting sensitivity analysis.</small> {data-background=#e6e6e6}





# <b>Overview of Shipping Labor</b> <br><small>Monthly Shipping Hours tracks most strongly with Monthly Case Production. <br><br>The following slides provide an exploratory summary of Total Monthly Shipping Hours by Warehouse, and are meant to supply context to consumers of this information.</small> {data-background=#e6e6e6}

## Distribution of Night Hours
```{r ship_hours_distribution, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=10, fig.height=6}
##HISTOGRAM LABOR HOURS
avgs_by_house = monthly_data %>% group_by(House) %>%
  summarise(Avg.of.Total.Monthly.Night.Labor = mean(Night.Ship.Hours))
kc_avg = as.numeric(avgs_by_house %>% filter(House == 'KC') %>% select(one_of=c(Avg.of.Total.Monthly.Night.Labor)))
stl_avg = as.numeric(avgs_by_house %>% filter(House == 'STL') %>% select(one_of=c(Avg.of.Total.Monthly.Night.Labor)))

p = ggplot(data=monthly_data, aes(x=Night.Ship.Hours, group=House, label=Month))
Night_Hours_Histogram = p + 
  geom_density(aes(fill=House), colour='black', alpha=0.5) + 
  scale_y_continuous(labels=percent) +
  scale_x_continuous(labels=comma) +
  theme(legend.position='none') +
  labs(title='Distribution of Monthly Shipping Labor Hours', y='% Distribution',
       x='Monthly Sum of Night Ship Hours by Warehouse') +
  geom_vline(xintercept=kc_avg, colour='red', alpha=0.6) +
  geom_vline(xintercept=stl_avg, colour='blue', alpha=0.6)

ggplotly(Night_Hours_Histogram)
```

## Monthly Shipping Hours
```{r ship_hours_timeseries, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=10, fig.height=6}
##TIME SERIES LABOR HOURS
p = ggplot(data=m, aes(x=Month, y=Night.Ship.Hours, group=House, label=Year.Month))
NIGHT_TIME_SERIES = p + 
  geom_bar(stat='identity',aes(fill=House), colour='black', alpha=0.5) + 
  # geom_point(aes(x=Month, y=Forecast.Ship.Hours[,1], group=House, size=Production.Days), 
  #            fill='black', alpha=0.5) + 
  scale_y_continuous(labels=comma) +
  theme(legend.position='none', axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title='Time Series of Total Monthly Shipping Labor Hours', y='Total Monthly Night Ship Hours',
       x='Month') +
  geom_smooth(colour='black', alpha=0.1) +
  facet_grid(House~Year, scales='free_y')

ggplotly(NIGHT_TIME_SERIES)

```















# <b>Demand Model, 1-3 Month</b> <br><small>This is a multi-variable predictive model that uses Percent Mark-Up, Production Days and Warehouse to predict Monthly Std. Cases Sold.<br><br>This model has an R-squared of 0.888, meaning 88.8% of the variation in Monthly Std. Cases Sold is explained by Warehouse, Mark-Up, and Ship Days.<br><br></small> {data-background=#e6e6e6}


## Demand Model: One-Three Month
<center><small>
$$Y_{CASESSOLD} = \beta_0 + \beta_{STL}*X_{STL} + \beta_{MARKUP}*X_{MARKUP} + \beta_{SHIPDAYS}*X_{SHIPDAYS}$$

where $$Y_{CASESSOLD}=MonthlyStdCasesSold$$ $$X_{STL} = {0, 1}$$ $$X_{MARKUP}=TotalCasesDelivered$$ $$X_{SHIPDAYS}=MonthlyShipDays$$ 

and $$\beta_{ALL}=CoefficientsDerivedFromData$$ $$\beta_{0}=yIntercept$$
</small></center><br/>

<!-- ## Demand Model: One-Three Month -->
<!-- <ul> -->
<!--   <li>R-Squared (adjusted) = 0.888</li> -->
<!--   <li>Modeled on house, cases shipped, and ship days</li> -->
<!--   <li>Model explains >90% of the variation in the data</li> -->
<!--   <li>Cases delivered can be derived from the demand model</li> -->
<!-- </ul> -->


## Demand Model: One-Three Month 
```{r night_ship_labor_plot, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=10, fig.height=6}
# ON AVERAGE WE WERE OFF BY BELOW
SQRT_MSE = sqrt(mean(abs(three_mo_demand_model$residuals^2)))


p = ggplot(data=M, aes(x=Mark.Up, y=Std.Cases.Sold, group=House, label=Year.Month))
DEMAND_PLOT_3MO = p + 
  geom_point(aes(colour=factor(House), size=(Std.Cases.Sold - Forecast.Demand.3.Mo[,1]))) + 
  scale_y_continuous(labels=comma) +
  scale_x_continuous(labels=percent) +
  theme(legend.position='none') +
  labs(x='%Markup = (Price-Cost)/Cost', y='Monthly Standard Cases Sold') +
  ggtitle('1-3 Month Demand Forecast (black) vs. Actual (by House & Production Days)') +
  geom_line(aes(x=Mark.Up, y=Forecast.Demand.3.Mo[,1])) +
  geom_ribbon(aes(group=House, ymin=Forecast.Demand.3.Mo[,2], ymax=Forecast.Demand.3.Mo[,3]), alpha=0.3) +
  geom_point(aes(x=Mark.Up, y=Forecast.Demand.3.Mo[,1]), colour='black', alpha=0.4) +
  facet_wrap(~Production.Days, ncol=3)
ggplotly(DEMAND_PLOT_3MO)
```

## Demand Model: One-Three Month
```{r 3d_plot, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=8, fig.height=6}
scatterplot3d(m$Mark.Up, m$Production.Days, m$Std.Cases.Sold, 
              color=as.numeric(m$House), angle=-205, main='3d-Scatterplot of 3 Month Demand Model',
              pch=19, xlab='Percent Mark Up', ylab='Production Days in Month', zlab='Monthly Std. Cases Sold')
```












# <b>Demand Model, 4-12 Month</b> <br><small>This is a single variable predictive model that uses Monthly Sales Projections/Budgets to predict Monthly Std. Cases Sold.<br><br>This model has an R-Squared of 0.929, meaning 92.9% of the variation in Monthly Std. Cases Sold is explained by our own projections.<br><br>This is less of a model and more of a correlation, reflecting that we do well getting close to our goals.</small> {data-background=#e6e6e6}


## Demand Model: Four-Twelve Month
```{r four_to_twelve_plot, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=10, fig.height=6}
## 4-12 MONTH DEMAND MODEL
four_to_twelve_demand_model = lm(monthly_data$Std.Cases.Sold ~ monthly_data$Sales.Projections)
xx = seq(min(monthly_data$Sales.Projections), max(monthly_data$Sales.Projections), by=10)
monthly_data$Forecast.Demand.12.Mo = predict(four_to_twelve_demand_model,
                                             data.frame(x=monthly_data$Sales.Projections), interval='p')

p = ggplot(data=monthly_data, aes(x=Sales.Projections, y=Std.Cases.Sold,#Cases.Delivered # to check 
                                  label=Over.Short.of.Projection))
DEMAND_PLOT_4MO = p + 
  geom_point(aes(colour=factor(Met.Sales.Goal), size=Cases.Delivered)) + 
  scale_y_continuous(labels=comma) +
  scale_x_continuous(labels=dollar) +
  theme(legend.position='bottom') +
  labs(x='Monthly Sales Projections by House', y='Monthly Standard Cases Sold') +
  ggtitle('Sales Projections as a Predictor of Monthly Demand (Cases)') +
  geom_line(aes(x=Sales.Projections, y=Forecast.Demand.12.Mo[,1])) +
  geom_ribbon(aes(ymin=Forecast.Demand.12.Mo[,2], ymax=Forecast.Demand.12.Mo[,3]), alpha=0.3) +
  theme(legend.position='none')

ggplotly(DEMAND_PLOT_4MO)
```






## Sales Projections vs. Actual
```{r cum_projection_plot, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=10, fig.height=6}
x = ggplot(data=monthly_data, aes(x=Month, y=Cumulative.Sales, group=House, label=Met.Sales.Goal))
CUMULATIVE_PROJECTION_PLOT = x + 
  geom_line(colour='black', size=1, alpha=0.5) +
  geom_point(colour='black', size=1, alpha=0.5) +
  geom_line(aes(x=Month, y=Cumulative.Projections, colour=House), size=3, alpha=0.3) +
  geom_point(aes(x=Month, y=Cumulative.Projections, colour=House), size=3, alpha=0.3) +
  scale_y_continuous(labels=dollar) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
        plot.title = element_text(lineheight=.8, face="bold"),
        legend.position='none') +
  facet_grid(~Year) +
  ggtitle('YTD Sales (black) vs. YTD Projections \nBy Warehouse & Year')

ggplotly(CUMULATIVE_PROJECTION_PLOT)
```














# <b>Production Model</b> <br><small>This model is a simple regression where Cases Sold is a predictor of Cases Produced.<br><br>This model is meant to translate how many cases we sell in a given month into how many cases we'll actually distribute to market in that same month.<br><br>This simple model has an R-squared of 0.859, meaning 85.9% of the variation in Cases Produced is explained by <i><b>our prediction of Demand</b></i>.</small> {data-background=#e6e6e6}

















# <b>Shipping Labor Model</b> <br><small>Hypothesis: Monthly shipping hours can be mathematically explained by Monthly Case Production, the Warehouse in question, and the number of Production Days in that month for that Warehouse.<br/><br/>Monthly Case Production is a function of Monthly Case Demand.<br><br></small> {data-background=#e6e6e6}



## Monthly Ship Hours Model
<center><small>
$$Y_{HOURS} = \beta_0 + \beta_{STL}*X_{STL} + \beta_{CASES}*X_{CASES} + \beta_{SHIPDAYS}*X_{SHIPDAYS}$$

where $$Y_{HOURS}=ShipHoursToPredict$$ $$X_{STL} = {0, 1}$$ $$X_{CASES}=TotalCasesDelivered$$ $$X_{SHIPDAYS}=MonthlyShipDays$$ 

and $$\beta_{ALL}=CoefficientsDerivedFromData$$ $$\beta_{0}=yIntercept$$


<br><br>
<b>This model explains 89% of the variance of Monthly Night Ship Hours around its mean.</b>

<b>This model is to be used for 1-3 month horizons (to adjust forecasts from teh 4-12 month model). This is because pricing is "set in stone" three months out, meaning we can access what our average mark-up will be. This will require a weighted average (simple calculation) prior to feeding into the model.</b>
</small></center><br/>





## Labor Model Fit
```{r ship_labor_plot, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=10, fig.height=6}
##PREDICTIVE LABOR MODEL
p = ggplot(data=monthly_data, aes(x=Cases.Delivered, y=Night.Ship.Hours, group=House, label=Year.Month))
Labor_Model_Plot = p + 
  geom_point(aes(colour=factor(House), size=Production.Days)) + 
  geom_smooth(method='lm',aes(group=House, colour=House), colour='black', alpha=0.1) +
  scale_y_continuous(labels=comma) +
  scale_x_continuous(labels=comma) +
  theme(legend.position='none') +
  labs(title='Predictive Model: Monthly Shipping Labor Hours', y='Monthly Night Ship Hours',
       x='Actual Cases Delivered')
ggplotly(Labor_Model_Plot)
```





## Model Prediction vs. Actual
```{r CLOSER_LABOR_MODEL_PLOT, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=10, fig.height=6}
##PREDICTIVE LABOR MODEL
p = ggplot(data=m, aes(x=Forecast.Production[,1], y=Night.Ship.Hours, group=House, label=Year.Month))
CLOSER_LABOR_MODEL = p + geom_point(aes(colour=factor(House), size=Production.Days)) + 
  facet_wrap(~Production.Days, ncol=4, scales='free') +
  scale_y_continuous(labels=comma) +
  scale_x_continuous(labels=comma) +
  theme(legend.position='none') +
  geom_point(aes(group=House, x=Forecast.Production[,1], y=Forecast.Ship.Hours[,1])) +
  geom_line(aes(group=House, x=Forecast.Production[,1], y=Forecast.Ship.Hours[,1])) +
  geom_ribbon(aes(group=House, ymin=Forecast.Ship.Hours[,2], ymax=Forecast.Ship.Hours[,3]), alpha=0.3) +
  labs(title='Predictive Model: Monthly Shipping Labor Hours', y='Monthly Night Ship Hours',
       x='Prediction of Cases Delivered')
ggplotly(CLOSER_LABOR_MODEL)
```





## Model Prediction vs. Actual
```{r BIGTIME_MODEL_, echo=FALSE, cache=FALSE, align='center', warning=FALSE, results=FALSE, message=FALSE, fig.width=10, fig.height=6}
##TIME SERIES LABOR HOURS
p = ggplot(data=m, aes(x=Month, y=Night.Ship.Hours, group=House, label=Year.Month))
NIGHT_TIME_SERIES = p + 
  geom_bar(stat='identity', fill='grey', colour='black', alpha=0.5) + 
  geom_point(aes(x=Month, y=Forecast.Ship.Hours[,1], group=House, size=Production.Days, fill=House), 
             fill='black', alpha=0.5) + 
  scale_y_continuous(labels=comma) +
  theme(legend.position='none', axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title='Time Series of Total Monthly Shipping Labor Hours', y='Total Monthly Night Ship Hours',
       x='Month') +
  geom_smooth(colour='black', alpha=0.1) +
  facet_grid(House~Year, scales='free_y')

ggplotly(NIGHT_TIME_SERIES)

```












  



# <b>Questions, Comments & Discussion</b> <br><small>Please take this time to clarify understanding, raise concerns, or provide input on the findings.<br><br>Thank you for your time!</small> {data-background=#e6e6e6}










# <b>Parting Words of Wisdom</b> <br><small>"The part that is stable we shall predict. The part that is unstable we shall control" -John von Neumann<br><br>"The day science begins to study non-physical phenomena, it will make more progress in one decade than in all the previous centuries of its existence." -Nikola Tesla <br><br>"Madness is rare in individuals-but in groups, parties, nations, and ages it is the rule" -Peter Thiel</small> {data-background=#e6e6e6}





















